### 2023-03-21 Analysis tests.Rmd
Update scraper + upload test analysis rmd
Updated the scraper to extract the address line. Additionally added code to copy the scraper into the site-packages or dist-packages directory of the machine.

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidygeocoder)
```

```{r}
df <- read_csv("funda_buy_17-03-2023.csv")
```

```{r}
model <- lm(data = df, price~room +living_area + house_age + house_type)
summary(model)
```

```{r}

df_new <- df %>% 
  top_n(10) %>% 
  mutate(adddreszip = paste0(address, ", Noord-Holland")) %>% 
  geocode(adddreszip, method = 'osm', lat = latitude , long = longitude)

```

```{r}
easypackages::packages ("sf", "sp", "spdep", "spatialreg", "GWmodel", "tmap", "mapview", "car", "RColorBrewer", 
                        "cowplot", "leafsync", "leaflet.extras2", "mapview", "tidyverse")

```

```{r}
library(sf)
df_sp <- df_new %>% drop_na()
x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
x <- st_transform(x, crs = 28992)
st_write(x, "test.gpkg")

```

```{r}

qtm(x)
```
```{r}
greendata_sp <- as_Spatial(x)

#fit the adaptive kernel 
#find adaptive kernel using gaussian function
abw <- bw.gwr(price~room +living_area + house_age,
             approach = "AIC", #specified by CV for cross-validation approach or by AIC corrected (AICc), we used AIC 
             adaptive = TRUE,
             kernel="gaussian", #this can be different function e.g., bisquare,exponential, depend on the prior understanding or choice of the modeler
             data=greendata_sp) #give the sp data created earlier
```

```{r}
#fitting the model with gwr.basic function
a.gwr <- gwr.basic(price~room +living_area + house_age, #the equation
             adaptive = TRUE,
             kernel="gaussian", #indicate the Kernel again
             bw = 17, #give the optimal bandwidth we found in the last stage
             data=greendata_sp)

#print the model result
a.gwr
```
```{r}
multiGWR <- gwr.multiscale(price~room +living_area + house_age, 
                        data = greendata_sp,
                        adaptive = T, 
                        max.iterations = 10, #usually large number to make sure each variable converage to best bandwidth
                        criterion="CVR", #criterion for determining the convergence of the back-fitting procedure
                        kernel = "bisquare", #kernel can also be gaussian, exponential
                        bws0=c(10,10,10), #starting number of neighbors  
                        verbose = F, predictor.centered=rep(T, 6)) 
```

```{r}
multiGWR
```

```{r}
library(leaflet)
leaflet(df_new) %>% addTiles() %>%
  addCircleMarkers(lng = ~longitude, lat = ~latitude, 
             popup = ~address)
```

### 2023-03-21 copy_scraper.py

@@ -1,0 +1,48 @@
+from distutils.dir_util import copy_tree
+import sys
+
+def query_yes_no(question, default="yes"):
+    """Ask a yes/no question via raw_input() and return their answer.
+
+    "question" is a string that is presented to the user.
+    "default" is the presumed answer if the user just hits <Enter>.
+            It must be "yes" (the default), "no" or None (meaning
+            an answer is required of the user).
+
+    The "answer" return value is True for "yes" or False for "no".
+    """
+    valid = {"yes": True, "y": True, "ye": True, "no": False, "n": False}
+    if default is None:
+        prompt = " [y/n] "
+    elif default == "yes":
+        prompt = " [Y/n] "
+    elif default == "no":
+        prompt = " [y/N] "
+    else:
+        raise ValueError("invalid default answer: '%s'" % default)
+
+    while True:
+        sys.stdout.write(question + prompt)
+        choice = input().lower()
+        if default is not None and choice == "":
+            return valid[default]
+        elif choice in valid:
+            return valid[choice]
+        else:
+            sys.stdout.write("Please respond with 'yes' or 'no' " "(or 'y' or 'n').\n")
+
+def get_package_path():
+  package_path = None
+  for i in sys.path:
+    if i.endswith('site-packages') or i.endswith('dist-packages'):
+        package_path = i
+  return package_path
+
+def copy_scraper():
+    answer = query_yes_no(f"Package will be placed in: {get_package_path()}, is this the correct package directory?"):
+    if answer:
+        copy_tree("Scraper_library", get_package_path())
+    elif answer != True:
+        path = input('Specify path or abort')
+        if path != "abort":
+            copy_tree("Scraper_library", path)

### 2023-03-21 Analysis tests.Rmd
MGWR first run

@@
 library(tidygeocoder)
+library(leaflet)
+library(sf)
+library(tmap)
+library(spatialreg)
+library(GWmodel)
+library(RColorBrewer)
+library(mapview)
+library(leafsync)
 ```
@@
 ```{r}
-df <- read_csv("funda_buy_17-03-2023.csv")
+df <- read_csv("data/funda_buy_21-03-2023(sample100p).csv")
+
+str(df)
+df <-  df %>% 
+  mutate(house_type = factor(house_type),
+         building_type = factor(building_type),
+         energy_label = factor(energy_label),
+         has_balcony = factor(has_balcony),
+         has_garden = factor(has_garden))
+str(df)
+
 ```
@@
 ```{r}
-model <- lm(data = df, price~room +living_area + house_age + house_type)
+model <- lm(data = df, price~room +living_area + house_age)
 summary(model)
@@
 ```{r}
+df_test <- df %>% 
+  top_n(10) %>% 
+  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
+  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
+         addressline_zip = paste(zip, letters),
+         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
+  select(-optional1, -optional2, -optional3, -optional4) %>% 
+  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
 
-df_new <- df %>% 
-  top_n(10) %>% 
-  mutate(adddreszip = paste0(address, ", Noord-Holland")) %>% 
-  geocode(adddreszip, method = 'osm', lat = latitude , long = longitude)
+```
+```{r}
 
+leaflet(df_new) %>% addTiles() %>%
+  addCircleMarkers(lng = ~longitude, lat = ~latitude, 
+             popup = ~address)
 ```
@@
 ```{r}
-easypackages::packages ("sf", "sp", "spdep", "spatialreg", "GWmodel", "tmap", "mapview", "car", "RColorBrewer", 
-                        "cowplot", "leafsync", "leaflet.extras2", "mapview", "tidyverse")
 
-```
-
-```{r}
-library(sf)
 df_sp <- df_new %>% drop_na()
@@
 x <- st_transform(x, crs = 28992)
-st_write(x, "test.gpkg")
-
+st_write(x, "data/test/test_sample(100p).gpkg")
+x <- st_read("data/test/test_sample(100p).gpkg")
 ```
@@
 ```
+
 ```{r}
@@
              kernel="gaussian", #indicate the Kernel again
-             bw = 17, #give the optimal bandwidth we found in the last stage
+             bw = 19, #give the optimal bandwidth we found in the last stage
              data=greendata_sp)
@@
                         criterion="CVR", #criterion for determining the convergence of the back-fitting procedure
-                        kernel = "bisquare", #kernel can also be gaussian, exponential
+                        kernel = "gaussian", #kernel can also be gaussian, exponential
                         bws0=c(10,10,10), #starting number of neighbors  
-                        verbose = F, predictor.centered=rep(T, 6)) 
+                        verbose = F, predictor.centered=rep(T, 6),
+                        parallel.method = "omp") 
 ```
@@
 ```{r}
-library(leaflet)
-leaflet(df_new) %>% addTiles() %>%
-  addCircleMarkers(lng = ~longitude, lat = ~latitude, 
-             popup = ~address)
+mgwr_sf = st_as_sf(multiGWR$SDF)
+st_write(mgwr_sf, "data/test/test_sample(100p)_predictions.gpkg")
 ```
+
+```{r}
+mgwrM1 <- mapview::mapview(mgwr_sf, zcol = "room", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
+mgwrM2 <- mapview::mapview(mgwr_sf, zcol = "living_area", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
+mgwrM3 <- mapview::mapview(mgwr_sf, zcol = "house_age", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
+```
+
+```{r}
+sync(mgwrM1, mgwrM2, mgwrM3)
+```

### 2023-03-21 Analysis tests.Rmd
Changed the README to come from and RMD file

@@
 ```{r}
-df <- read_csv("data/funda_buy_21-03-2023(sample100p).csv")
+df <- read_csv("data/test/funda_buy_21-03-2023(sample100p).csv")
 
@@
 ```{r}
-df_test <- df %>% 
-  top_n(10) %>% 
+df_new <- df %>% 
   separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
@@
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
+write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
 

### 2023-03-21 README.Rmd
Changed the README to come from and RMD file

---
title: "Explaining Noord-Holland house prices"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
date: "2023-03-21"
output: github_document
---

```{=html}
<style type="text/css">
  body{
  font-size: 12pt;
  font-family:Cambria;
  text-align: justify;
}
headers{
text-align: left;

}
</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# "Explaining Noord-Holland house prices"

A Spatial Statistics and Spatial Machine Learning approach.

Included data of the research was scraped from Funda. Below map gives an overview of the scope of the data.

```{r}
library(leaflet)
df <- read.csv('data/test/funda_buy_21-03-2023(sample100p)latlon.csv')

leaflet(df) %>% addTiles() %>%
  addCircleMarkers(lng = ~longitude, lat = ~latitude, 
             popup = ~address)
```

### 2023-03-23 copy_scraper.py
removed bug

@@ -39,7 +39,7 @@ def get_package_path():
   return package_path
 
 def copy_scraper():
-    answer = query_yes_no(f"Package will be placed in: {get_package_path()}, is this the correct package directory?"):
+    answer = query_yes_no(f"Package will be placed in: {get_package_path()}, is this the correct package directory?")
     if answer:
         copy_tree("Scraper_library", get_package_path())
     elif answer != True:

### 2023-03-23 Scraper/Scraper_library/funda_scraper/config/core.py
organized folders

@@ -1,0 +1,16 @@
+"""Configuration used for scraping """
+
+from pathlib import Path
+
+from diot import Diot
+import yaml
+from yaml.loader import SafeLoader
+import funda_scraper
+
+PACKAGE_ROOT = Path(funda_scraper.__file__).resolve().parent
+CONFIG_PATH = PACKAGE_ROOT / "config/config.yaml"
+
+with open(CONFIG_PATH) as f:
+    data = yaml.load(f, Loader=SafeLoader)
+
+config = Diot(data)

### 2023-03-23 Scraper/Scraper_library/funda_scraper/preprocess.py

@@ -1,0 +1,194 @@
+"""Preprocess raw data scraped from Funda"""
+from typing import Any
+
+import pandas as pd
+from funda_scraper.config.core import config
+from datetime import datetime
+from datetime import timedelta
+
+
+def clean_price(x: str) -> int:
+    """Clean the 'price' and transform from string to integer."""
+    try:
+        return int(str(x).split(" ")[1].replace(",", ""))
+    except ValueError:
+        return 0
+    except IndexError:
+        return 0
+
+
+def clean_year(x: str) -> int:
+    """Clean the 'year' and transform from string to integer"""
+    if len(x) == 4:
+        return int(x)
+    elif x.find("-") != -1:
+        return int(x.split("-")[0])
+    elif x.find("before") != -1:
+        return int(x.split(" ")[1])
+    else:
+        return 0
+
+
+def clean_living_area(x: str) -> int:
+    """Clean the 'living_area' and transform from string to integer"""
+    try:
+        return int(str(x).replace(",", "").split(" m²")[0])
+    except ValueError:
+        return 0
+    except IndexError:
+        return 0
+
+
+def find_n_room(x: str) -> int:
+    """Find the number of rooms from a string"""
+    if x.find("room") != -1:
+        return int(str(x).split("room")[0].strip())
+    else:
+        return 0
+
+
+def find_n_bedroom(x: str) -> int:
+    """Find the number of bedrooms from a string"""
+    if x.find("bedroom") != -1:
+        return int(x.split(" ")[2].replace("(", ""))
+    else:
+        return 0
+
+
+def find_n_bathroom(x: str) -> int:
+    """Find the number of bathrooms from a string"""
+    if x.find("bathroom") != -1:
+        return int(str(x).split("bathroom")[0].strip())
+    else:
+        return 0
+
+
+def map_dutch_month(x: str) -> str:
+    """Map the month from Dutch to English."""
+    month_mapping = {
+        "januari": "January",
+        "februari": "February",
+        "maart": "March",
+        "mei": "May",
+        "juni": "June",
+        "juli": "July",
+        "augustus": "August",
+        "oktober": "October",
+    }
+    for k, v in month_mapping.items():
+        if x.find(k) != -1:
+            x = x.replace(k, v)
+    return x
+
+
+def get_neighbor(x: str) -> str:
[…]

### 2023-03-23 Scraper/Scraper_library/funda_scraper/scrape.py

@@ -1,0 +1,244 @@
+"""Main funda scraper module"""
+import multiprocessing as mp
+import os
+import pandas as pd
+import requests
+from bs4 import BeautifulSoup
+from typing import List, Dict
+import datetime
+from funda_scraper.config.core import config
+from funda_scraper.preprocess import preprocess_data
+from funda_scraper.utils import logger
+from tqdm import tqdm
+from tqdm.contrib.concurrent import process_map
+
+
+class FundaScraper:
+    """
+    Handles the main scraping function.
+    """
+
+    def __init__(
+        self,
+        area: str = None,
+        want_to: str = "buy",
+        n_pages: int = 1,
+        find_past: bool = False,
+    ):
+        self.area = area.lower().replace(" ", "-") if isinstance(area, str) else area
+        self.want_to = want_to
+        self.find_past = find_past
+        self.n_pages = min(max(n_pages, 1), 999)
+        self.links: List[str] = []
+        self.raw_df = pd.DataFrame()
+        self.clean_df = pd.DataFrame()
+        self.base_url = config.base_url
+        self.selectors = config.css_selector
+
+    def __repr__(self):
+        return (
+            f"FundaScraper(area={self.area}, "
+            f"want_to={self.want_to}, "
+            f"n_pages={self.n_pages}, "
+            f"use_past_data={self.find_past})"
+        )
+
+    @property
+    def site_url(self) -> Dict[str, str]:
+        """Return the corresponding urls."""
+        if self.to_buy:
+            return {
+                "close": f"{self.base_url}/koop/verkocht/{self.area}/",
+                "open": f"{self.base_url}/koop/{self.area}/",
+            }
+        else:
+            return {
+                "close": f"{self.base_url}/huur/{self.area}/verhuurd/",
+                "open": f"{self.base_url}/huur/{self.area}/",
+            }
+
+    @property
+    def to_buy(self) -> bool:
+        """Whether to buy or not"""
+        if self.want_to.lower() in ["buy", "koop", "b"]:
+            return True
+        elif self.want_to.lower() in ["rent", "huur", "r"]:
+            return False
+        else:
+            raise ValueError("'want_to' must be 'either buy' or 'rent'.")
+
+    @staticmethod
+    def _check_dir() -> None:
+        """Check whether a temporary directory for data"""
+        if not os.path.exists("data"):
+            os.makedirs("data")
+
+    @staticmethod
+    def _get_links_from_one_page(url: str) -> List[str]:
+        """Scrape all the available housing items from one Funda search page."""
[…]

### 2023-03-23 Scraper/Scraper_library/funda_scraper/utils.py

@@ -1,0 +1,37 @@
+"""Utilities for modules"""
+import logging
+
+
+class CustomFormatter(logging.Formatter):
+
+    grey = "\x1b[38;20m"
+    yellow = "\x1b[33;20m"
+    red = "\x1b[31;20m"
+    bold_red = "\x1b[31;1m"
+    reset = "\x1b[0m"
+    format = "%(asctime)s - %(levelname)s - %(message)s (%(filename)s:%(lineno)d)"
+
+    FORMATS = {
+        logging.DEBUG: grey + format + reset,
+        logging.INFO: grey + format + reset,
+        logging.WARNING: yellow + format + reset,
+        logging.ERROR: red + format + reset,
+        logging.CRITICAL: bold_red + format + reset,
+    }
+
+    def format(self, record):
+        log_fmt = self.FORMATS.get(record.levelno)
+        formatter = logging.Formatter(log_fmt)
+        return formatter.format(record)
+
+
+logger = logging.getLogger("funda_scraper")
+logger.setLevel(logging.INFO)
+
+# # create console handler with a higher log level
+ch = logging.StreamHandler()
+ch.setLevel(logging.INFO)
+
+ch.setFormatter(CustomFormatter())
+
+logger.addHandler(ch)

### 2023-03-23 Scraper/copy_scraper.py

@@ -1,0 +1,48 @@
+from distutils.dir_util import copy_tree
+import sys
+
+def query_yes_no(question, default="yes"):
+    """Ask a yes/no question via raw_input() and return their answer.
+
+    "question" is a string that is presented to the user.
+    "default" is the presumed answer if the user just hits <Enter>.
+            It must be "yes" (the default), "no" or None (meaning
+            an answer is required of the user).
+
+    The "answer" return value is True for "yes" or False for "no".
+    """
+    valid = {"yes": True, "y": True, "ye": True, "no": False, "n": False}
+    if default is None:
+        prompt = " [y/n] "
+    elif default == "yes":
+        prompt = " [Y/n] "
+    elif default == "no":
+        prompt = " [y/N] "
+    else:
+        raise ValueError("invalid default answer: '%s'" % default)
+
+    while True:
+        sys.stdout.write(question + prompt)
+        choice = input().lower()
+        if default is not None and choice == "":
+            return valid[default]
+        elif choice in valid:
+            return valid[choice]
+        else:
+            sys.stdout.write("Please respond with 'yes' or 'no' " "(or 'y' or 'n').\n")
+
+def get_package_path():
+  package_path = None
+  for i in sys.path:
+    if i.endswith('site-packages') or i.endswith('dist-packages'):
+        package_path = i
+  return package_path
+
+def copy_scraper():
+    answer = query_yes_no(f"Package will be placed in: {get_package_path()}, is this the correct package directory?")
+    if answer:
+        copy_tree("Scraper_library", get_package_path())
+    elif answer != True:
+        path = input('Specify path or abort')
+        if path != "abort":
+            copy_tree("Scraper_library", path)

### 2023-03-23 Scraper_library/funda_scraper/__init__.py

@@ -1,3 +1,0 @@
-"""Access the directory in python"""
-from funda_scraper.scrape import FundaScraper
-

### 2023-03-23 Scraper_library/funda_scraper/config/core.py

@@ -1,16 +1,0 @@
-"""Configuration used for scraping """
-
-from pathlib import Path
-
-from diot import Diot
-import yaml
-from yaml.loader import SafeLoader
-import funda_scraper
-
-PACKAGE_ROOT = Path(funda_scraper.__file__).resolve().parent
-CONFIG_PATH = PACKAGE_ROOT / "config/config.yaml"
-
-with open(CONFIG_PATH) as f:
-    data = yaml.load(f, Loader=SafeLoader)
-
-config = Diot(data)

### 2023-03-23 Scraper_library/funda_scraper/preprocess.py

@@ -1,194 +1,0 @@
-"""Preprocess raw data scraped from Funda"""
-from typing import Any
-
-import pandas as pd
-from funda_scraper.config.core import config
-from datetime import datetime
-from datetime import timedelta
-
-
-def clean_price(x: str) -> int:
-    """Clean the 'price' and transform from string to integer."""
-    try:
-        return int(str(x).split(" ")[1].replace(",", ""))
-    except ValueError:
-        return 0
-    except IndexError:
-        return 0
-
-
-def clean_year(x: str) -> int:
-    """Clean the 'year' and transform from string to integer"""
-    if len(x) == 4:
-        return int(x)
-    elif x.find("-") != -1:
-        return int(x.split("-")[0])
-    elif x.find("before") != -1:
-        return int(x.split(" ")[1])
-    else:
-        return 0
-
-
-def clean_living_area(x: str) -> int:
-    """Clean the 'living_area' and transform from string to integer"""
-    try:
-        return int(str(x).replace(",", "").split(" m²")[0])
-    except ValueError:
-        return 0
-    except IndexError:
-        return 0
-
-
-def find_n_room(x: str) -> int:
-    """Find the number of rooms from a string"""
-    if x.find("room") != -1:
-        return int(str(x).split("room")[0].strip())
-    else:
-        return 0
-
-
-def find_n_bedroom(x: str) -> int:
-    """Find the number of bedrooms from a string"""
-    if x.find("bedroom") != -1:
-        return int(x.split(" ")[2].replace("(", ""))
-    else:
-        return 0
-
-
-def find_n_bathroom(x: str) -> int:
-    """Find the number of bathrooms from a string"""
-    if x.find("bathroom") != -1:
-        return int(str(x).split("bathroom")[0].strip())
-    else:
-        return 0
-
-
-def map_dutch_month(x: str) -> str:
-    """Map the month from Dutch to English."""
-    month_mapping = {
-        "januari": "January",
-        "februari": "February",
-        "maart": "March",
-        "mei": "May",
-        "juni": "June",
-        "juli": "July",
-        "augustus": "August",
-        "oktober": "October",
-    }
-    for k, v in month_mapping.items():
-        if x.find(k) != -1:
-            x = x.replace(k, v)
-    return x
-
-
-def get_neighbor(x: str) -> str:
[…]

### 2023-03-23 Scraper_library/funda_scraper/scrape.py

@@ -1,244 +1,0 @@
-"""Main funda scraper module"""
-import multiprocessing as mp
-import os
-import pandas as pd
-import requests
-from bs4 import BeautifulSoup
-from typing import List, Dict
-import datetime
-from funda_scraper.config.core import config
-from funda_scraper.preprocess import preprocess_data
-from funda_scraper.utils import logger
-from tqdm import tqdm
-from tqdm.contrib.concurrent import process_map
-
-
-class FundaScraper:
-    """
-    Handles the main scraping function.
-    """
-
-    def __init__(
-        self,
-        area: str = None,
-        want_to: str = "buy",
-        n_pages: int = 1,
-        find_past: bool = False,
-    ):
-        self.area = area.lower().replace(" ", "-") if isinstance(area, str) else area
-        self.want_to = want_to
-        self.find_past = find_past
-        self.n_pages = min(max(n_pages, 1), 999)
-        self.links: List[str] = []
-        self.raw_df = pd.DataFrame()
-        self.clean_df = pd.DataFrame()
-        self.base_url = config.base_url
-        self.selectors = config.css_selector
-
-    def __repr__(self):
-        return (
-            f"FundaScraper(area={self.area}, "
-            f"want_to={self.want_to}, "
-            f"n_pages={self.n_pages}, "
-            f"use_past_data={self.find_past})"
-        )
-
-    @property
-    def site_url(self) -> Dict[str, str]:
-        """Return the corresponding urls."""
-        if self.to_buy:
-            return {
-                "close": f"{self.base_url}/koop/verkocht/{self.area}/",
-                "open": f"{self.base_url}/koop/{self.area}/",
-            }
-        else:
-            return {
-                "close": f"{self.base_url}/huur/{self.area}/verhuurd/",
-                "open": f"{self.base_url}/huur/{self.area}/",
-            }
-
-    @property
-    def to_buy(self) -> bool:
-        """Whether to buy or not"""
-        if self.want_to.lower() in ["buy", "koop", "b"]:
-            return True
-        elif self.want_to.lower() in ["rent", "huur", "r"]:
-            return False
-        else:
-            raise ValueError("'want_to' must be 'either buy' or 'rent'.")
-
-    @staticmethod
-    def _check_dir() -> None:
-        """Check whether a temporary directory for data"""
-        if not os.path.exists("data"):
-            os.makedirs("data")
-
-    @staticmethod
-    def _get_links_from_one_page(url: str) -> List[str]:
-        """Scrape all the available housing items from one Funda search page."""
[…]

### 2023-03-23 Scraper_library/funda_scraper/utils.py

@@ -1,37 +1,0 @@
-"""Utilities for modules"""
-import logging
-
-
-class CustomFormatter(logging.Formatter):
-
-    grey = "\x1b[38;20m"
-    yellow = "\x1b[33;20m"
-    red = "\x1b[31;20m"
-    bold_red = "\x1b[31;1m"
-    reset = "\x1b[0m"
-    format = "%(asctime)s - %(levelname)s - %(message)s (%(filename)s:%(lineno)d)"
-
-    FORMATS = {
-        logging.DEBUG: grey + format + reset,
-        logging.INFO: grey + format + reset,
-        logging.WARNING: yellow + format + reset,
-        logging.ERROR: red + format + reset,
-        logging.CRITICAL: bold_red + format + reset,
-    }
-
-    def format(self, record):
-        log_fmt = self.FORMATS.get(record.levelno)
-        formatter = logging.Formatter(log_fmt)
-        return formatter.format(record)
-
-
-logger = logging.getLogger("funda_scraper")
-logger.setLevel(logging.INFO)
-
-# # create console handler with a higher log level
-ch = logging.StreamHandler()
-ch.setLevel(logging.INFO)
-
-ch.setFormatter(CustomFormatter())
-
-logger.addHandler(ch)

### 2023-03-23 copy_scraper.py

@@ -1,48 +1,0 @@
-from distutils.dir_util import copy_tree
-import sys
-
-def query_yes_no(question, default="yes"):
-    """Ask a yes/no question via raw_input() and return their answer.
-
-    "question" is a string that is presented to the user.
-    "default" is the presumed answer if the user just hits <Enter>.
-            It must be "yes" (the default), "no" or None (meaning
-            an answer is required of the user).
-
-    The "answer" return value is True for "yes" or False for "no".
-    """
-    valid = {"yes": True, "y": True, "ye": True, "no": False, "n": False}
-    if default is None:
-        prompt = " [y/n] "
-    elif default == "yes":
-        prompt = " [Y/n] "
-    elif default == "no":
-        prompt = " [y/N] "
-    else:
-        raise ValueError("invalid default answer: '%s'" % default)
-
-    while True:
-        sys.stdout.write(question + prompt)
-        choice = input().lower()
-        if default is not None and choice == "":
-            return valid[default]
-        elif choice in valid:
-            return valid[choice]
-        else:
-            sys.stdout.write("Please respond with 'yes' or 'no' " "(or 'y' or 'n').\n")
-
-def get_package_path():
-  package_path = None
-  for i in sys.path:
-    if i.endswith('site-packages') or i.endswith('dist-packages'):
-        package_path = i
-  return package_path
-
-def copy_scraper():
-    answer = query_yes_no(f"Package will be placed in: {get_package_path()}, is this the correct package directory?")
-    if answer:
-        copy_tree("Scraper_library", get_package_path())
-    elif answer != True:
-        path = input('Specify path or abort')
-        if path != "abort":
-            copy_tree("Scraper_library", path)

### 2023-03-23 Yúri/osm_data.R
OSM keys

@@ -1,0 +1,26 @@
+easypackages::packages("sf", "sp", "osmdata")
+
+read_sf("C:/Users/ygrin/Documents/GitHub/Noord_Holland_house_prices/Yúri/data/Noord_holland_polygon.shp") %>%
+  st_transform(crs=4326) %>%
+  st_write("Noord_Holland.gpkg", )
+
+province_boundaries <- st_read ("C:/Users/ygrin/Documents/GitHub/Noord_Holland_house_prices/Yúri/data/Noord_Holland.gpkg")
+
+# Get OSM data
+bus <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("bus_station")) %>%
+  osmdata_sf ()
+bus_points <- st_as_sf (bus$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+
+subway <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "railway", c("subway_entrance")) %>%
+  osmdata_sf ()
+subway_points <- st_as_sf (subway$osm_points) %>% dplyr:: select(osm_id)
+
+
+train <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "building", c("train_station")) %>%
+  osmdata_sf ()
+train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
+

### 2023-03-23 Yúri/osm_data.R
Update osm_data.R

@@ -24,3 +24,33 @@ train <-  opq(st_bbox(province_boundaries)) %>%
   osmdata_sf ()
 train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
 
+############################################################ DISTANCES ###########################################################
+#Re-project the point layer from WGS to local projection to have unit in meter
+bikefac_points <-  st_transform (bikefac_points, 27700)
+
+#Re-project the point layer from WGS to local projection to have unit in meter
+shop_points <-  st_transform (Dailyshops_points, 27700)
+
+#now we would write our own function to estimate distance using nearest neighbor algorithm
+#This function take an origin point (from), and a destination point (to), and then use nn function of FNN package to estimate the distance to the nearest (k =1) neighborhood location
+nn_function <- function(measureFrom,measureTo,k) {
+  measureFrom_Matrix <- as.matrix(measureFrom)
+  measureTo_Matrix <- as.matrix(measureTo)
+  nn <-   
+    get.knnx(measureTo, measureFrom, k)$nn.dist [,k]
+  return(nn)
+}
+
+#now we will use the nn_function to measure the shortest distance from neighborhood centroid to  bike facilities (i.e., bikefac_points)
+#distance to bike facilities (shops, repair, parking)
+greendatacen <- greendatacen %>%
+  mutate(bikefac_dist_new = nn_function(st_coordinates(greendatacen$geom), st_coordinates(bikefac_points$geom), 1))
+
+#distance to shops
+greendatacen <- greendatacen %>%
+  mutate(Shop_dist_new = nn_function(st_coordinates(greendatacen$geom), st_coordinates(shop_points$geom), 1))
+
+#you can see the data frame and there is new column at the end.
+#view(greendatacen)
+
+#this is how you can convert the raw OSM data into a spatial indicator

### 2023-03-23 Analysis tests.Rmd
Created a notebook to run the MGWR and write it in a geopackage in the same format as the R output

@@
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
-write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
-
+#write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
+#df_new %>% 
+#  select(longitude, latitude, price, room, living_area, house_age) %>% 
+#  write.csv("data/test/mgwr.csv")
 ```
@@
 ```{r}
-multiGWR <- gwr.multiscale(price~room +living_area + house_age, 
+EUDM <- gw.dist(coordinates(greendata_sp))
+
+multiGWR_test <- gwr.multiscale(price~room +living_area + house_age, 
                         data = greendata_sp,
-                        adaptive = T, 
-                        max.iterations = 10, #usually large number to make sure each variable converage to best bandwidth
+                        max.iterations = 1,
+                        adaptive = T,  #usually large number to make sure each variable converage to best bandwidth
                         criterion="CVR", #criterion for determining the convergence of the back-fitting procedure
                         kernel = "gaussian", #kernel can also be gaussian, exponential
-                        bws0=c(10,10,10), #starting number of neighbors  
-                        verbose = F, predictor.centered=rep(T, 6),
-                        parallel.method = "omp") 
+                        bws0 =c(93,48,46,70),
+                        bw.seled = c(T,T,T,T), dMats=list(EUDM,EUDM,EUDM)) 
+```
+```{r}
+gwr.predict(multiGWR_test, data = )
 ```
@@
 ```{r}
-mgwr_sf = st_as_sf(multiGWR$SDF)
-st_write(mgwr_sf, "data/test/test_sample(100p)_predictions.gpkg")
+#mgwr_sf = st_as_sf(multiGWR$SDF)
+#mgwr_sf <- st_read("test_sample(100p)_predictions")
+mgwr_sf <- st_read("data/test/test_mgwr.gpkg")
+
 ```
@@
 mgwrM3 <- mapview::mapview(mgwr_sf, zcol = "house_age", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
+mgwrM4 <- mapview::mapview(mgwr_sf, zcol = "residual", col.regions= brewer.pal(11, "PuOr"), map.type = "CartoDB.Positron")
 ```
@@
 ```{r}
-sync(mgwrM1, mgwrM2, mgwrM3)
+sync(mgwrM1, mgwrM2, mgwrM3,mgwrM4)
 ```

### 2023-03-23 Datalore/dataloader.py
Create dataloader.py

@@ -1,0 +1,8 @@
+import pandas as pd
+import geopandas as gp
+
+def load_csv_data(dir):
+    return pd.read_csv(dir)
+
+def load_csv_data(dir):
+    return gp.read_file(dir)

### 2023-03-23 Datalore/dataloader.py
Delete dataloader.py

@@ -1,8 +1,0 @@
-import pandas as pd
-import geopandas as gp
-
-def load_csv_data(dir):
-    return pd.read_csv(dir)
-
-def load_csv_data(dir):
-    return gp.read_file(dir)

### 2023-03-24 Yúri/osm_data.R
osm update

@@ -1,10 +1,11 @@
 easypackages::packages("sf", "sp", "osmdata")
 
-read_sf("C:/Users/ygrin/Documents/GitHub/Noord_Holland_house_prices/Yúri/data/Noord_holland_polygon.shp") %>%
-  st_transform(crs=4326) %>%
-  st_write("Noord_Holland.gpkg", )
+#read_sf("data/Noord_holland_polygon.shp") %>%
+ # st_transform(crs=4326) %>%
+  #st_write("Noord_Holland.gpkg", )
 
-province_boundaries <- st_read ("C:/Users/ygrin/Documents/GitHub/Noord_Holland_house_prices/Yúri/data/Noord_Holland.gpkg")
+province_boundaries <- st_read ("data/Noord_Holland.gpkg")
+funda_data <- st_read ("data/test_sample(100p).gpkg")
 
 # Get OSM data
 bus <-  opq(st_bbox(province_boundaries)) %>%
@@ -26,12 +27,10 @@ train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
 
 ############################################################ DISTANCES ###########################################################
 #Re-project the point layer from WGS to local projection to have unit in meter
-bikefac_points <-  st_transform (bikefac_points, 27700)
+bus_points <-  st_transform (bus_points, 28992)
+subway_points <-  st_transform (subway_points, 28992)
+train_points <-  st_transform (train_points, 28992)
 
-#Re-project the point layer from WGS to local projection to have unit in meter
-shop_points <-  st_transform (Dailyshops_points, 27700)
-
-#now we would write our own function to estimate distance using nearest neighbor algorithm
 #This function take an origin point (from), and a destination point (to), and then use nn function of FNN package to estimate the distance to the nearest (k =1) neighborhood location
 nn_function <- function(measureFrom,measureTo,k) {
   measureFrom_Matrix <- as.matrix(measureFrom)
@@ -41,16 +40,14 @@ nn_function <- function(measureFrom,measureTo,k) {
   return(nn)
 }
 
-#now we will use the nn_function to measure the shortest distance from neighborhood centroid to  bike facilities (i.e., bikefac_points)
-#distance to bike facilities (shops, repair, parking)
-greendatacen <- greendatacen %>%
-  mutate(bikefac_dist_new = nn_function(st_coordinates(greendatacen$geom), st_coordinates(bikefac_points$geom), 1))
+#distance to bus stop
[…]

### 2023-03-24 Yúri/osm_data.R
distances

@@ -1,4 +1,5 @@
-easypackages::packages("sf", "sp", "osmdata")
+easypackages::packages("sf", "sp", "osmdata", "FNN")
+library(dplyr)
 
 #read_sf("data/Noord_holland_polygon.shp") %>%
  # st_transform(crs=4326) %>%
@@ -51,3 +52,5 @@ funda_data <- funda_data %>%
 #distance to train station
 funda_data <- funda_data %>%
   mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train_points$geom), 1))
+
+st_write(funda_data, "data/test_sample_distances(100p).gpkg")

### 2023-03-29 Analysis tests.Rmd
update structure

@@
 ```{r}
-df <- read_csv("data/test/funda_buy_21-03-2023(sample100p).csv")
+df <- read_csv("Scraper/data/funda_buy_28-03-2023_full.csv")
 
@@
 ```{r}
-model <- lm(data = df, price~room +living_area + house_age)
+model <- lm(data = df, price~ house_type + building_type + room + bedroom + bathroom + living_area + energy_label +has_balcony + has_garden + house_age)
 summary(model)
@@
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
-#write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
+#write.csv(df_new,"data/funda_buy_28-03-2023_full_latlon.csv")
 #df_new %>% 
@@
 ```
+```{r}
+#write.csv(df_new,"data/funda_buy_28-03-2023_full_latlon.csv")
+#df_sp <- df_new %>% drop_na()
+#x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
+#x <- st_transform(x, crs = 28992)
+#st_write(x, "data/funda_buy_28-03-2023_full.gpkg")
+
+```
+
 ```{r}
@@
 
-df_sp <- df_new %>% drop_na()
-x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
-x <- st_transform(x, crs = 28992)
-st_write(x, "data/test/test_sample(100p).gpkg")
-x <- st_read("data/test/test_sample(100p).gpkg")
+#df_sp <- df_new %>% drop_na()
+#x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
+#x <- st_transform(x, crs = 28992)
+#st_write(x, "data/test/test_sample(100p).gpkg")
+#x <- st_read("data/test/test_sample(100p).gpkg")
 ```

### 2023-03-29 1a. Pre-processing.R

@@ -1,0 +1,27 @@
+###Important to specify correct names for the original data and the desination data
+
+#specify paths
+origin_path <- "Scraper/data/"
+desination_path <-  "data/"
+
+#below names need to be specified
+
+orgin_df_name <- "SPECIFY_THIS.csv"
+desination_df_name <- "SPECIFY_THIS.csv"
+desination_gpkg_name <- "SPECIFY_THIS.gkpg"
+
+#load raw scraped Funda data from the folder
+
+df <- read.csv(paste0(origin_path, orgin_df_name))
+
+#show and adjust structure
+str(df)
+df <-  df %>% 
+  mutate(house_type = factor(house_type),
+         building_type = factor(building_type),
+         energy_label = factor(energy_label),
+         has_balcony = factor(has_balcony),
+         has_garden = factor(has_garden))
+str(df)
+
+

### 2023-03-29 1b. Data enrichment.R
Update

@@ -1,0 +1,109 @@
+easypackages::packages("sf", "sp", "osmdata", "FNN")
+library(dplyr)
+
+#read_sf("data/Noord_holland_polygon.shp") %>%
+# st_transform(crs=4326) %>%
+#st_write("Noord_Holland.gpkg", )
+
+# POIs: school, university, hospital/clinic, shopping center/mall, train, subway, bus, supermarket/market
+
+province_boundaries <- st_read ("data/Noord_Holland.gpkg")
+funda_data <- st_read ("data/funda_buy_28-03-2023_full.gpkg")
+
+# Get OSM data
+bus <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("bus_station")) %>%
+  osmdata_sf ()
+bus_points <- st_as_sf (bus$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+
+subway <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "railway", c("subway_entrance")) %>%
+  osmdata_sf ()
+subway_points <- st_as_sf (subway$osm_points) %>% dplyr:: select(osm_id)
+
+
+train <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "building", c("train_station")) %>%
+  osmdata_sf ()
+train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+university <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("university")) %>%
+  osmdata_sf ()
+university_points <- st_as_sf (university$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+school <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("school")) %>%
+  osmdata_sf ()
+school_points <- st_as_sf (school$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+hospital <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("hospital")) %>%
+  osmdata_sf ()
+hospital_points <- st_as_sf (hospital$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+mall <-  opq(st_bbox(province_boundaries)) %>%
+  add_osm_feature(key = "shop", c("mall")) %>%
[…]

### 2023-03-29 Yúri/osm_data.R

@@ -8,7 +8,7 @@ library(dplyr)
 # POIs: school, university, hospital/clinic, shopping center/mall, train, subway, bus, supermarket/market
 
 province_boundaries <- st_read ("data/Noord_Holland.gpkg")
-funda_data <- st_read ("data/test_sample(100p).gpkg")
+funda_data <- st_read ("data/funda_buy_28-03-2023_full.gpkg")
 
 # Get OSM data
 bus <-  opq(st_bbox(province_boundaries)) %>%
@@ -106,4 +106,4 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
   mutate(supermarket_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(supermarket_points$geom), 1))
 
-#st_write(funda_data, "data/test_sample_distances(100p).gpkg")
+st_write(funda_data, "data/funda_buy_28-03-2023_full_distances.gpkg")

### 2023-03-29 1b. Data enrichment.R
Update 1b. Data enrichment.R

@@ -106,4 +106,5 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
   mutate(supermarket_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(supermarket_points$geom), 1))
 
+#write results to updated gpkg
 st_write(funda_data, "data/funda_buy_28-03-2023_full_distances.gpkg")

### 2023-03-29 1a. Pre-processing.R
Preprocessing script

@@ -1,6 +1,8 @@
 ###Important to specify correct names for the original data and the desination data
 
-#specify paths
+
+easypackages::packages("raster", "sf", "tidyverse", "tidygeocoder", "mapview")
+#paths
 origin_path <- "Scraper/data/"
 desination_path <-  "data/"
 
@@ -8,7 +10,7 @@ desination_path <-  "data/"
 
 orgin_df_name <- "SPECIFY_THIS.csv"
 desination_df_name <- "SPECIFY_THIS.csv"
-desination_gpkg_name <- "SPECIFY_THIS.gkpg"
+desination_gpkg_name <- "SPECIFY_THIS.gpkg"
 
 #load raw scraped Funda data from the folder
 
@@ -23,5 +25,38 @@ df <-  df %>%
          has_balcony = factor(has_balcony),
          has_garden = factor(has_garden))
 str(df)
+
+#create correct address-line based on the funda data
+#geocode the addres line with OSM to lat long columns
+
+df_geo <- df %>% 
+  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
+  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4, optional5),
+         addressline_zip = paste(zip, letters),
+         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
+  select(-optional1, -optional2, -optional3, -optional4, -optional5) %>% 
+  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
+
+#wire to csv
+write.csv(df_geo, paste0(desination_path, desination_df_name))
+df_geo <- read_csv("data/funda_buy_28-03-2023_full_latlon.csv")
+#write to geopackage 
+
+#NAs will be dropped and the data will be clipped to Noord-Holland to delete any falsely geocoded locations.
+
+df_geo_clean <- df_geo %>% drop_na() 
+
+df_spatial = st_as_sf(df_geo_clean, coords = c( "longitude", "latitude"), crs = 4326)
+#transform to RDNEW
+df_spatial <- st_transform(df_spatial, crs = 28992)
+
+#clip data bases on NH boundary
+df_spatial_clipped <- st_intersection(df_spatial, st_transform(st_read("data/Noord_Holland.gpkg"), crs = 28992))
+
+#view data
+mapview(df_spatial_clipped)
+
+#write to geopackage
+st_write(df_spatial_clipped,paste0(desination_path, desination_gpkg_name))
 
 

### 2023-03-30 1b. Data enrichment.R
update code

@@ -1,5 +1,4 @@
-easypackages::packages("sf", "sp", "osmdata", "FNN")
-library(dplyr)
+easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse")
 
 #read_sf("data/Noord_holland_polygon.shp") %>%
 # st_transform(crs=4326) %>%

### 2023-03-30 2a. OLS & SAC.R

@@ -1,0 +1,92 @@
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
+
+#load data
+funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
+
+
+funda_data <- funda_data %>% filter(price <1000000)
+
+
+#plot dependent variable
+mapview(funda_data, zcol = "price", col.regions=brewer.pal(20, "YlOrRd"))
+
+
+tm_shape(funda_data) +
+  tm_dots(c("price", "living_area")) + 
+  tm_layout(legend.position = c("right", "top"), 
+            legend.text.size = 0.5, legend.title.size = 0.8)
+
+
+
+
+
+
+
+
+
+
+
+
+
+### PC4 test
+
+PC4 <- st_transform(st_read("data/Postcodevlakken_PC_4/PC4.shp"), crs= 28992)
+Noord_Holland <- st_transform(st_read("data/Noord_Holland.gpkg"), crs= 28992)
+
+
+NH_PC4 <- st_intersection(PC4, Noord_Holland)
+
+mapview(NH_PC4, zcol = "PC4", col.regions=brewer.pal(9, "YlOrRd"))
+
+Mode <- function(x) {
+  ux <- unique(x) 
+  ux[which.max(tabulate(match(x, ux)))]} 
+
+funda_agg <- funda_data %>% 
+  mutate(zip = as.character(zip)) %>% 
+  group_by(zip) %>% 
+  summarize(price = median(price),
+            percent_house = sum(house_type=="huis")/n() * 100,
+            building_type = Mode(building_type),
+            room = median(room),
+            bedroom = median(bedroom),
+            bathroom = median(bathroom),
+            energy_label = Mode(energy_label),
+            living_area = median(living_area),
+            house_area = median(house_age),
+            has_garden = Mode(has_garden),
+            has_balcony = Mode(has_balcony),
+            house_age = median(house_age),
+            bus_dist = median(bus_dist),
+            subway_dist = median(subway_dist),
+            train_dist = median(train_dist),
+            university_dist = median(university_dist),
+            school_dist = median(school_dist),
+            mall_dist = median(mall_dist),
+            supermarket_dist = median(supermarket_dist)) %>% 
+  st_drop_geometry() %>%
+  left_join(NH_PC4, by = c("zip"="PC4"))
+
[…]

### 2023-03-30 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -1,21 +1,49 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg")
 
 #load data
 funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
-
-
-funda_data <- funda_data %>% filter(price <1000000)
-
+#funda_data <- funda_data %>% filter(price <1000000)
 
 #plot dependent variable
-mapview(funda_data, zcol = "price", col.regions=brewer.pal(20, "YlOrRd"))
-
+mapview(funda_data, zcol = "price", col.regions=brewer.pal(9, "YlOrRd"))
 
 tm_shape(funda_data) +
   tm_dots(c("price", "living_area")) + 
   tm_layout(legend.position = c("right", "top"), 
             legend.text.size = 0.5, legend.title.size = 0.8)
 
+#test global spatial autocorrelation with Moran's I
+funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
+funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
+funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
+mc_global_knn <- moran.mc(funda_data$price, funda_KNN_w, 2999, alternative="greater")
+plot(mc_global_knn)
+mc_global_knn
+#there is significant spatial autocorrelation
+
+equation <- price ~ room + bedroom + bathroom + living_area + house_age + bus_dist + subway_dist + 
+  train_dist + university_dist + school_dist + mall_dist + supermarket_dist + house_type +
+  building_type + energy_label + has_balcony + has_garden
+#OLS
+model <- lm(equation, 
+            data = funda_data)
+summary(model)
+#check multicollinearity (VIF < 5)
+vif(model)
+#homoscedasticity test using plots 
+par(mfrow=c(2,2))
+plot(model)
+#test spatial autocorrelation in residuals
+mc_global_OLS <- moran.mc(model$residuals, funda_KNN_w, 2999, zero.policy= TRUE, alternative="greater")
+#plot the  Moran’s I
+plot(mc_global_OLS)
+mc_global_OLS
+#Now plot the residuals
[…]

### 2023-03-30 2a. OLS & SAC.R
update gwr model

@@ -1,4 +1,4 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync")
 
 #load data
 funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
@@ -52,6 +52,29 @@ summary(sac_model, Nagelkerke=T)
 
 
 
+
+
+
+
+
+
+
+
+
+
+
+
+gwr_result<- st_read("data/gwr_results_full.gpkg")
+
+
+bus <- mapview(gwr_result, zcol = "university_dist", col.regions=brewer.pal(9, "YlOrRd"))
+train <- mapview(gwr_result, zcol = "train_dist", col.regions=brewer.pal(9, "YlOrRd"))
+subway <- mapview(gwr_result, zcol = "subway_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+bus
+
+gwr_result %>% 
+  ggplot(aes(x = residual)) + geom_density()
 
 
 ########### KNOEIEN

### 2023-03-30 2a. OLS & SAC.R
cleaned repository

@@ -67,11 +67,9 @@ summary(sac_model, Nagelkerke=T)
 gwr_result<- st_read("data/gwr_results_full.gpkg")
 
 
-bus <- mapview(gwr_result, zcol = "university_dist", col.regions=brewer.pal(9, "YlOrRd"))
-train <- mapview(gwr_result, zcol = "train_dist", col.regions=brewer.pal(9, "YlOrRd"))
-subway <- mapview(gwr_result, zcol = "subway_dist", col.regions=brewer.pal(9, "YlOrRd"))
+map <- mapview(gwr_result, zcol = "living_area_TV", col.regions=brewer.pal(9, "YlOrRd"))
 
-bus
+map
 
 gwr_result %>% 
   ggplot(aes(x = residual)) + geom_density()

### 2023-03-30 README.Rmd
update readme

@@
 
-```{=html}
-<style type="text/css">
-  body{
-  font-size: 12pt;
-  font-family:Cambria;
-  text-align: justify;
-}
-headers{
-text-align: left;
-
-}
-</style>
-```
-
 ```{r setup, include=FALSE}
@@
 ```
-
-# "Explaining Noord-Holland house prices"
 
@@
 
-```{r}
-library(leaflet)
-df <- read.csv('data/test/funda_buy_21-03-2023(sample100p)latlon.csv')
+## We used the Funda-Scraper package to scrape our data
 
-leaflet(df) %>% addTiles() %>%
-  addCircleMarkers(lng = ~longitude, lat = ~latitude, 
-             popup = ~address)
+The query we used for the Funda-Scraper with below query on 28-03-2023.
+
+```{python eval = FALSE}
+scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False, n_pages = 1000)
+df = scraper.run()
 ```
+Note that this is not the original Funda-Scraper code underneath.
+The Function is adjusted to contain additional adress information, compared to the origional function.
+Code is included in the Scraper.ipynb file to copy the updated package into the site-packages directory of python.
+
+## A pre-processing pipeline is used to enrich data
+
+OSM was used to enrich the scraped data. We geocode adressess into geometries objects for in order to make use of the geospatial models.
+Additional spatial data includes:
+
+*Distance to public transport (Bus, Subway, and Train)
+*Distance to public services (Schools, Universities, Shopping centres)
+
+## This enriched data is used to fit an OLS model
+
+### OLS on scraped data
+
+```{r eval = FALSE}
+model <- lm(price~ room + bedroom + bathroom + living_area + house_age, data = funda_data)
+```
+
+### OLS on enriched data
+
+```{r eval = FALSE}
+model <- lm(price~ room + bedroom + bathroom + living_area + house_age + bus_dist +subway_dist + train_dist + university_dist + school_dist + mall_dist + supermarket_dist, data = funda_data)
+```
+
+### GWR model to adjust for spatial component in the data
+
+To look at local spatial dependence, a GWR model was fit on the data.
+
+```{python eval = FALSE}
+#Run basic GWR in parallel mode
+
+gwr_selector = Sel_BW(b_coords, b_y, b_X)
+gwr_bw = gwr_selector.search(pool = pool)
+print(gwr_bw)
+gwr_results = GWR(b_coords, b_y, b_X, gwr_bw).fit(pool = pool)
+
+```
+
+### MGWR model to adjust for spatial component in the data
+
+As it would be more realistic to have different band-widths for every feature, MGWR was used
+
+```{python eval = FALSE}
+#run MGWR in parallel mode. Note: max_iter_multi needs to be specified
+
+mgwr_selector = Sel_BW(b_coords, b_y, b_X, multi=True)
+mgwr_bw = mgwr_selector.search(pool=pool, max_iter_multi=200, criterion = "AICc") 
+print(mgwr_bw)
+mgwr_results = MGWR(b_coords, b_y, b_X, selector=mgwr_selector).fit(pool=pool)
+
+```

### 2023-03-30 2a. OLS & SAC.R

@@ -67,7 +67,7 @@ summary(sac_model, Nagelkerke=T)
 gwr_result<- st_read("data/gwr_results_full.gpkg")
 
 
-map <- mapview(gwr_result, zcol = "living_area_TV", col.regions=brewer.pal(9, "YlOrRd"))
+map <- mapview(gwr_result, zcol = "house_age", col.regions=brewer.pal(9, "YlOrRd"))
 
 map
 

### 2023-03-30 Paper/paper.Rmd
Start with paper layout

---
title: "Explaining Noord-Holland house prices"
author: 
  - Yúri Grings
  - Thomas Nibbering
  - Jitse Ruurd Nauta
date: "2023-03-21"

output: 
    pdf_document:
        latex_engine: xelatex
mainfont: Cambria
classoption:
- twocolumn
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)

```

# 1. Abstract
In an effort to create a green and diversified energy system, the Dutch national government aims to stimulate the adoption of renewables. In this context, wind energy is considered to be one of the most promising. However, the potential of this type of renewable is greatly influenced by existing land-use claims and related spatial and social policies. It becomes clear that, shifting to wind energy as a renewable energy source is a key challenge in densely populated countries, such as the Netherlands. Therefore, this study aims to examine the energy potential of suitable onshore wind farm sites in the province of North-Holland. In order to identify suitable areas for the placement of wind turbines, several spatial and social criteria and constraints were considered in three scenarios using a multi-criteria decision analysis method. Based on a power density function, the total energy potential of the suitable areas was determined. The results of the scenarios ranged from 2 MW to 3017 MW of prospective energy generable. These large ranges of potential show the significant impact of constraints and criteria and underline the need for a comprehensive understanding of the relationship between site suitability and spatial policies and choices.

# 2. Introduction
One of the aims of the Dutch national government is to stimulate renewables in order to create a green and diversified energy system [1]. Among the several alternatives available, wind energy is considered to be one of the most promising due to its limited environmental impact and economic viability [2]. Despite the advantages, wind energy still plays a marginal role in the total Dutch energy consumption [3]. While various reasons can be identified, this small share mainly relates to the fact that wind energy has to compete with other spatial claims that may be deemed more important.

Under the current legal framework, provinces are largely responsible for shaping spatial and energy plans [4]. However, the allocation for this type of renewable poses significant challenges. Apart from technical and physical incompatibility that influences the onshore location of wind farms, societal and environmental considerations are similarly important. Nature and other valuable landscapes often have a protected status, limiting or at least constraining the allocation of wind farms [5]. Moreover, societal resistance to environmental impact experienced by those near wind turbines also inspire spatial energy policies and choices [6]. As a result, the transition to onshore wind turbines as a source of renewable energy represents a key challenge in a country that is as densely populated as the Netherlands.

A review of literature revealed that there is a multitude of studies that aimed to identify the spatial potential for wind energy deployment. Often studies applied geospatial information systems in combination with a multi-criteria decision analysis to examine the suitability of sites [2, 7]. Here, areas of interest were evaluated based on a variety of criteria and constraints. In general, these studies employed a rule-based approach considering mostly physical [8], economic [9, 10] and environmental [2] aspects with only a few placing emphasis on social considerations [11, 12]. Moreover, the literature revealed that studies using a scenario-based approach were limited, especially in the Netherlands [13]. As a result, a comprehensive understanding of the relationship between site suitability for wind farms and multiple spatial policies and choices remain underdeveloped.

In an effort to examine the energy potential of sites suitable for the production of wind energy, mathematical functions are the main tools used in literature [14]. Among the several types available, wind power density is most commonly employed [15–17]. Although several studies have proven its limitations in wind energy assessment due to its flexibility and simplicity, the method is widely accepted and can be considered almost a standard approach [18, 19].

Based on the examined literature, multi-criteria decision analysis in combination with a wind power density function emerges as an effective tool for assessing the energy potential of sites suitable for the production of wind energy. Given the limited literature available on wind farm allocation in the Netherlands and the evident challenges associated with balancing elements of interest, this study aims to provide a preliminary overview of the energy potential of suitable onshore wind farm sites in the province of North-Holland.

# 3. Methods
## 3.1 Study Area
In this study, the geographical scope was limited to the province of North-Holland, as presented in Figure 1. The area is situated in the North-Western part of the Netherlands and occupies an onshore space of 2,840 km2 [5]. The province is home to almost 2,8 million inhabitants, making it one of the most densely populated regions in the country (684 inhabitants/km2) [20]. Outside the large urban areas, the vast majority of the land is agricultural with two areas designated as National Parks [20, 21]. At the moment, the province is obligated by the Dutch national government to have an extra installed onshore wind capacity of 105.5 MW [4, 5].

```{r include=FALSE}
library(mapview)
library(tidyverse)
library(tmap)
library(sf)
setwd("./..")
funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
setwd("Paper")
```

Plot klein

```{r test1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()
```

\onecolumn
of plot groot

```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()
```

Bron vermelding zo:
@fotheringham2017multiscale

Of zo:
[-@fotheringham2017multiscale]

# References

<div id="refs"></div>

### 2023-03-30 README.Rmd
update readme
Start with paper layout

@@
 date: "2023-03-21"
+
 output: github_document
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
+
 ```
@@
 
-Included data of the research was scraped from Funda. Below map gives an overview of the scope of the data.
+Below the structure, results, and some code of our research can be found.
+
+Kind regards,
+
+Yúri Grings [Linkedin](https://www.linkedin.com/in/yurigrings/), Thomas Nibbering [Linkedin](https://www.linkedin.com/in/thomas-nibbering/), Jitse Ruurd Nauta [Linkedin](https://www.linkedin.com/in/jitseruurdnauta/)
 
@@
 
-The query we used for the Funda-Scraper with below query on 28-03-2023.
+The query below was used to scrape our final research data on (28-03-2023).
 
 ```{python eval = FALSE}
-scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False, n_pages = 1000)
+scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False,\
+n_pages = 1000)
 df = scraper.run()
@@
 
-*Distance to public transport (Bus, Subway, and Train)
-*Distance to public services (Schools, Universities, Shopping centres)
+* Distance to public transport (Bus, Subway, and Train)
+* Distance to public services (Schools, Universities, Shopping centres)
 

### 2023-03-30 Paper/paper.Rmd
paper layout update

@@
 
+```{r include=FALSE}
+library(mapview)
+library(tidyverse)
+library(tmap)
+library(sf)
+setwd("./..")
+funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
+setwd("Paper")
+```
+
 # 1. Abstract
@@
 These large ranges of potential show the significant impact of constraints and criteria and underline the need for a comprehensive understanding of the relationship between site suitability and spatial policies and choices.
+
+Plot in text
+
+```{r test3, message=FALSE, warning=FALSE, include=FALSE}
+pdf("figures/plot.pdf")
+tm_shape(funda_data) +
+  tm_dots(c("price", "living_area"))
+dev.off()
+```
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
+  \caption{This is a figure.}
+\end{figure*}
 
@@
 
-```{r include=FALSE}
-library(mapview)
-library(tidyverse)
-library(tmap)
-library(sf)
-setwd("./..")
-funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
-setwd("Paper")
-```
-
 Plot klein
@@
   tm_dots()
+
+```
+
+```{r foo, out.width="100%", fig.cap="An example image.", include=FALSE, echo=FALSE}
+knitr::include_graphics("figures/plot.pdf")
 ```
@@
 
-```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
+```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Plot of NH full page"}
 tm_shape(funda_data) +

### 2023-03-31 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -2,18 +2,22 @@ easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "ca
 
 #load data
 funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
+nh_shape <- st_transform(st_read("data/Noord_Holland.gpkg"), crs = 28992)
 #funda_data <- funda_data %>% filter(price <1000000)
 
 #plot dependent variable
-mapview(funda_data, zcol = "price", col.regions=brewer.pal(9, "YlOrRd"))
+mapview(funda_data, zcol = "price_log", col.regions=brewer.pal(9, "YlOrRd"))
 
-tm_shape(funda_data) +
-  tm_dots(c("price", "living_area")) + 
+tm_shape(nh_shape) + 
+  tm_polygons() + 
+  tm_shape(funda_data) +
+  tm_dots(col = "price", breaks = c(0,100000,250000,500000,1000000,2500000,10000000)) + 
   tm_layout(legend.position = c("right", "top"), 
-            legend.text.size = 0.5, legend.title.size = 0.8)
+            legend.text.size = 0.5, legend.title.size = 0.8,
+            legend.outside = T)
 
 #test global spatial autocorrelation with Moran's I
-funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
+funda_KNN <- knearneigh(funda_data, k=10) #Identify k nearest neighbours for spatial weights 
 funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
 funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
 mc_global_knn <- moran.mc(funda_data$price, funda_KNN_w, 2999, alternative="greater")
@@ -22,8 +26,8 @@ mc_global_knn
 #there is significant spatial autocorrelation
 
 equation <- price ~ room + bedroom + bathroom + living_area + house_age + bus_dist + subway_dist + 
-  train_dist + university_dist + school_dist + mall_dist + supermarket_dist + house_type +
-  building_type + energy_label + has_balcony + has_garden
+  train_dist + university_dist + school_dist + mall_dist + supermarket_dist #+ house_type +
+  #building_type + energy_label + has_balcony + has_garden
 #OLS
[…]

### 2023-03-31 1a. Pre-processing.R
Update 1a. Pre-processing.R

@@ -8,9 +8,9 @@ desination_path <-  "data/"
 
 #below names need to be specified
 
-orgin_df_name <- "SPECIFY_THIS.csv"
-desination_df_name <- "SPECIFY_THIS.csv"
-desination_gpkg_name <- "SPECIFY_THIS.gpkg"
+orgin_df_name <- "funda_buy_amsterdam_31-03-2023_full.csv"
+desination_df_name <- "funda_buy_amsterdam_31-03-2023_fulllatlon.csv"
+desination_gpkg_name <- "funda_buy_amsterdam_31-03-2023_full.gpkg"
 
 #load raw scraped Funda data from the folder
 
@@ -30,16 +30,16 @@ str(df)
 #geocode the addres line with OSM to lat long columns
 
 df_geo <- df %>% 
-  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
+  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4", "optional5"), " ") %>% 
   mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4, optional5),
          addressline_zip = paste(zip, letters),
-         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
+         addresszip = paste0(address, ", ",addressline_zip, ", ", addressline_city)) %>% 
   select(-optional1, -optional2, -optional3, -optional4, -optional5) %>% 
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
 
 #wire to csv
 write.csv(df_geo, paste0(desination_path, desination_df_name))
-df_geo <- read_csv("data/funda_buy_28-03-2023_full_latlon.csv")
+
 #write to geopackage 
 
 #NAs will be dropped and the data will be clipped to Noord-Holland to delete any falsely geocoded locations.
@@ -51,12 +51,14 @@ df_spatial = st_as_sf(df_geo_clean, coords = c( "longitude", "latitude"), crs = 
 df_spatial <- st_transform(df_spatial, crs = 28992)
 
 #clip data bases on NH boundary
-df_spatial_clipped <- st_intersection(df_spatial, st_transform(st_read("data/Noord_Holland.gpkg"), crs = 28992))
+df_spatial_clipped <- st_intersection(df_spatial, st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992))
 
[…]

### 2023-03-31 1b. Data enrichment.R
Update 1b. Data enrichment.R

@@ -107,3 +107,35 @@ funda_data <- funda_data %>%
 
 #write results to updated gpkg
 st_write(funda_data, "data/funda_buy_28-03-2023_full_distances.gpkg")
+
+
+##### Amsterdam
+nn_function <- function(measureFrom,measureTo,k) {
+  measureFrom_Matrix <- as.matrix(measureFrom)
+  measureTo_Matrix <- as.matrix(measureTo)
+  nn <-   
+    get.knnx(measureTo, measureFrom, k)$nn.dist [,k]
+  return(nn)
+}
+amsterdam_boundaries <- st_transform(st_read("data/Amsterdam/PC4.json"), crs= 28992)
+
+amsterdam_network <- st_transform(st_read("data/Amsterdam/streets.json"), crs= 28992)
+public_transport <- st_transform(st_read("data/Amsterdam/public_transport.json"), crs= 28992)
+
+tram <- public_transport %>% 
+  filter(Modaliteit == "Tram")
+metro <- public_transport %>% 
+  filter(Modaliteit == "Metro")
+
+
+funda_data <- st_read ("data/funda_buy_amsterdam_31-03-2023_full.gpkg")
+
+funda_data <- funda_data %>%
+  mutate(tram_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(tram$geometry), 1))
+
+funda_data <- funda_data %>%
+  mutate(metro_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(metro$geometry), 1))
+
+
+#write results to updated gpkg
+st_write(funda_data, "data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")

### 2023-03-31 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -1,23 +1,22 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync")
 
 #load data
-funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
-nh_shape <- st_transform(st_read("data/Noord_Holland.gpkg"), crs = 28992)
+funda_data <- st_read("data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 #funda_data <- funda_data %>% filter(price <1000000)
 
 #plot dependent variable
-mapview(funda_data, zcol = "price_log", col.regions=brewer.pal(9, "YlOrRd"))
+mapview(funda_data, zcol = "price", col.regions=brewer.pal(9, "YlOrRd"))
 
-tm_shape(nh_shape) + 
-  tm_polygons() + 
-  tm_shape(funda_data) +
-  tm_dots(col = "price", breaks = c(0,100000,250000,500000,1000000,2500000,10000000)) + 
+tm_shape(PC4)+
+  tm_polygons()+
+tm_shape(funda_data)+
+  tm_dots(c("price"), style = "log10_pretty") + 
   tm_layout(legend.position = c("right", "top"), 
-            legend.text.size = 0.5, legend.title.size = 0.8,
-            legend.outside = T)
+            legend.text.size = 0.5, legend.title.size = 0.8)
 
 #test global spatial autocorrelation with Moran's I
-funda_KNN <- knearneigh(funda_data, k=10) #Identify k nearest neighbours for spatial weights 
+funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
 funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
 funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
 mc_global_knn <- moran.mc(funda_data$price, funda_KNN_w, 2999, alternative="greater")
@@ -25,9 +24,7 @@ plot(mc_global_knn)
 mc_global_knn
 #there is significant spatial autocorrelation
 
-equation <- price ~ room + bedroom + bathroom + living_area + house_age + bus_dist + subway_dist + 
[…]

### 2023-03-31 1b. Data enrichment.R
update

@@ -8,6 +8,7 @@ easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse")
 
 province_boundaries <- st_read ("data/Noord_Holland.gpkg")
 funda_data <- st_read ("data/funda_buy_28-03-2023_full.gpkg")
+trein <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
 
 # Get OSM data
 bus <-  opq(st_bbox(province_boundaries)) %>%
@@ -20,12 +21,6 @@ subway <-  opq(st_bbox(province_boundaries)) %>%
   add_osm_feature(key = "railway", c("subway_entrance")) %>%
   osmdata_sf ()
 subway_points <- st_as_sf (subway$osm_points) %>% dplyr:: select(osm_id)
-
-
-train <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "building", c("train_station")) %>%
-  osmdata_sf ()
-train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
 
 university <-  opq(st_bbox(province_boundaries)) %>%
   add_osm_feature(key = "amenity", c("university")) %>%
@@ -83,7 +78,7 @@ funda_data <- funda_data %>%
 
 #distance to train station
 funda_data <- funda_data %>%
-  mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train_points$geom), 1))
+  mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(trein$geometry), 1))
 
 #distance to university
 funda_data <- funda_data %>%
@@ -122,6 +117,11 @@ amsterdam_boundaries <- st_transform(st_read("data/Amsterdam/PC4.json"), crs= 28
 amsterdam_network <- st_transform(st_read("data/Amsterdam/streets.json"), crs= 28992)
 public_transport <- st_transform(st_read("data/Amsterdam/public_transport.json"), crs= 28992)
 
+trein <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
+
+
+
+
 tram <- public_transport %>% 
   filter(Modaliteit == "Tram")
 metro <- public_transport %>% 
@@ -136,6 +136,11 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
[…]

### 2023-03-31 2a. OLS & SAC.R

@@ -67,10 +67,14 @@ summary(sac_model, Nagelkerke=T)
 
 
 
-gwr_result<- st_read("data/gwr_results_full.gpkg")
+gwr_result<- st_read("data/gwr_results_amsterdam.gpkg")
 
+gwr_result %>% 
+  filter(living_area_TV < -1.96| living_area_TV > 1.96) %>% 
+  mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
+  
 
-map <- mapview(gwr_result, zcol = "house_age", col.regions=brewer.pal(9, "YlOrRd"))
+map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))
 
 map
 

### 2023-03-31 1b. Data enrichment.R
Update

@@ -6,11 +6,12 @@ easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse")
 
 # POIs: school, university, hospital/clinic, shopping center/mall, train, subway, bus, supermarket/market
 
+############################################################ NOORD-HOLLAND #######################################################
+############################################################ DATA ##########################################################
 province_boundaries <- st_read ("data/Noord_Holland.gpkg")
 funda_data <- st_read ("data/funda_buy_28-03-2023_full.gpkg")
-trein <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
-
-# Get OSM data
+train <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
+############################################################ OSM ###########################################################
 bus <-  opq(st_bbox(province_boundaries)) %>%
   add_osm_feature(key = "amenity", c("bus_station")) %>%
   osmdata_sf ()
@@ -46,9 +47,7 @@ supermarket <-  opq(st_bbox(province_boundaries)) %>%
   add_osm_feature(key = "shop", c("supermarket")) %>%
   osmdata_sf ()
 supermarket_points <- st_as_sf (supermarket$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-
-############################################################ DISTANCES ###########################################################
+############################################################ DISTANCES #####################################################
 #Re-project the point layer from WGS to local projection to have unit in meter
 bus_points <-  st_transform (bus_points, 28992)
 subway_points <-  st_transform (subway_points, 28992)
@@ -78,7 +77,7 @@ funda_data <- funda_data %>%
 
 #distance to train station
 funda_data <- funda_data %>%
-  mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(trein$geometry), 1))
+  mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train$geometry), 1))
 
 #distance to university
 funda_data <- funda_data %>%
@@ -104,7 +103,18 @@ funda_data <- funda_data %>%
 st_write(funda_data, "data/funda_buy_28-03-2023_full_distances.gpkg")
 
 
-##### Amsterdam
[…]

### 2023-03-31 2a. OLS & SAC.R
update

@@ -49,27 +49,6 @@ sac_model = sacsarlm(equation, data = funda_data, listw= funda_KNN_w, zero.polic
 summary(sac_model, Nagelkerke=T)
 
 
-#Visualize results GWR model
-gwr_result<- st_read("data/gwr_results_amsterdam.gpkg")
-
-gwr_result %>% 
-  filter(living_area_TV < -1.96| living_area_TV > 1.96) %>% 
-  mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
-  
-
-map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))
-
-map
-
-gwr_result %>% 
-  ggplot(aes(x = residual)) + geom_density()
-
-
-
-
-
-
-
 
 
 

### 2023-03-31 3. Final analysis & Results.R

@@ -1,0 +1,27 @@
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap")
+
+
+#Visualize results GWR model
+gwr_result<- st_read("data/gwr_results_full.gpkg")
+
+gwr_result %>% 
+  #filter(train_dist_TV < -1.96| train_dist_TV > 1.96) %>% 
+  mapview( zcol = "residual", col.regions=brewer.pal(9, "YlOrRd"))
+
+
+map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))
+
+map
+
+gwr_result %>% 
+  ggplot(aes(x = residual)) + geom_density()
+
+funda_data <- st_read("data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
+
+tm_shape(PC4)+
+  tm_polygons()+
+  tm_shape(gwr_result)+
+  tm_dots(c("train_dist")) + 
+  tm_layout(legend.position = c("right", "top"), 
+            legend.text.size = 0.5, legend.title.size = 0.8)

### 2023-03-31 3. Final analysis & Results.R
mgwr

@@ -2,11 +2,11 @@ easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap")
 
 
 #Visualize results GWR model
-gwr_result<- st_read("data/gwr_results_full.gpkg")
+gwr_result<- st_read("data/mgwr_results_amsterdam.gpkg")
 
 gwr_result %>% 
-  #filter(train_dist_TV < -1.96| train_dist_TV > 1.96) %>% 
-  mapview( zcol = "residual", col.regions=brewer.pal(9, "YlOrRd"))
+  filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
+  mapview( zcol = "tram_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
 
 map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))

### 2023-04-03 3. Final analysis & Results.R
Update 3. Final analysis & Results.R

@@ -8,6 +8,19 @@ gwr_result %>%
   filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
   mapview( zcol = "tram_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
+gwr_result %>% 
+  filter(train_dist_TV < -1.96| train_dist_TV > 1.96) %>% 
+  mapview( zcol = "train_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(metro_dist_TV < -1.96| metro_dist_TV > 1.96) %>% 
+  mapview( zcol = "metro_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(living_area_TV < -1.96| living_area_TV > 1.96) %>% 
+  mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
+
+
 
 map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))
 

### 2023-04-03 1c. Data enrichment.R
network

@@ -105,9 +105,9 @@ st_write(funda_data, "data/funda_buy_28-03-2023_full_distances.gpkg")
 
 ############################################################ AMSTERDAM ###########################################################
 ############################################################ DATA ###########################################################
-funda_data <- st_read ("data/funda_buy_amsterdam_31-03-2023_full.gpkg")
+funda_data <- st_transform(st_read("data/funda_buy_amsterdam_31-03-2023_full.gpkg"), crs = 28992)
 amsterdam_boundaries <- st_transform(st_read("data/Amsterdam/PC4.json"), crs= 28992)
-amsterdam_network <- st_transform(st_read("data/Amsterdam/streets.json"), crs= 28992)
+
 public_transport <- st_transform(st_read("data/Amsterdam/public_transport.json"), crs= 28992)
 tram <- public_transport %>% 
   filter(Modaliteit == "Tram")
@@ -135,5 +135,60 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
   mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train$geometry), 1))
 
+
+
+
+
 #write results to updated gpkg
 st_write(funda_data, "data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+
+############################################################ Network ######################################################
+
+easypackages::packages("sfnetworks", "tidygraph")
+
+amsterdam_network <- as_sfnetwork(st_transform(st_read("data/Amsterdam/streets.json"), crs= 28992))
+plot(amsterdam_network)
+
+facilities <- tram %>% st_geometry()
+sites <- funda_data %>% st_geometry() 
+
+net <- amsterdam_network %>%
+  activate("edges") %>%
+  mutate(weight = edge_length())
+
+plot(net)
+
+new_net = net %>%
+  activate("nodes") %>%
+  filter(group_components() == 1) %>%
+  st_network_blend(c(sites, facilities))
+
+
+plot(blended)
+
+cost_matrix = st_network_cost(new_net, from = snapped_sites %>% st_geometry(), to = snapped_facilities %>% st_geometry(), weights = "weight")
+
+facilities <- tram %>% st_geometry() 
+
+closest = facilities[apply(cost_matrix, 1, function(x) which(x == min(x))[1])]
+
+
[…]

### 2023-04-03 1c. Data enrichment.R
Update 1c. Data enrichment.R

@@ -135,12 +135,27 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
   mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train$geometry), 1))
 
+############################################################ NDVI ######################################################
+
+raster <- 
+
+
+terra::extract(raster, points)
 
 
 
 
 #write results to updated gpkg
 st_write(funda_data, "data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+
+
+
+
+
+
+
+
 
 
 ############################################################ Network ######################################################

### 2023-04-03 1a. Pre-processing.R
update ndvi + restructure

@@ -4,7 +4,7 @@
 easypackages::packages("raster", "sf", "tidyverse", "tidygeocoder", "mapview")
 #paths
 origin_path <- "Scraper/data/"
-desination_path <-  "data/"
+desination_path <-  "data/Houseprices"
 
 #below names need to be specified
 

### 2023-04-03 1c. Data enrichment.R

@@ -1,4 +1,56 @@
-easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse")
+easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse", "stars")
+
+############################################################ AMSTERDAM ###########################################################
+############################################################ DATA ###########################################################
+funda_data <- st_transform(st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full.gpkg"), crs = 28992)
+amsterdam_boundaries <- st_transform(st_read("data/Amsterdam/PC4.json"), crs= 28992)
+
+public_transport <- st_transform(st_read("data/Amsterdam/public_transport.json"), crs= 28992)
+tram <- public_transport %>% 
+  filter(Modaliteit == "Tram")
+metro <- public_transport %>% 
+  filter(Modaliteit == "Metro")
+
+train <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
+############################################################ DISTANCES ######################################################
+nn_function <- function(measureFrom,measureTo,k) {
+  measureFrom_Matrix <- as.matrix(measureFrom)
+  measureTo_Matrix <- as.matrix(measureTo)
+  nn <-   
+    get.knnx(measureTo, measureFrom, k)$nn.dist [,k]
+  return(nn)
+}
+
+funda_data <- funda_data %>%
+  mutate(tram_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(tram$geometry), 1))
+
+funda_data <- funda_data %>%
+  mutate(metro_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(metro$geometry), 1))
+
+funda_data <- funda_data %>%
+  mutate(metro_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(metro$geometry), 1))
+
+funda_data <- funda_data %>%
+  mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train$geometry), 1))
+
+############################################################ NDVI ######################################################
+
+
+raster100 <- read_stars("data/Greenness/NDVI_Amsterdam_100m.tif")
+raster300 <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
+raster500 <- read_stars("data/Greenness/NDVI_Amsterdam_500m.tif")
+
[…]

### 2023-04-03 3. Final analysis & Results.R

@@ -2,7 +2,7 @@ easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap")
 
 
 #Visualize results GWR model
-gwr_result<- st_read("data/mgwr_results_amsterdam.gpkg")
+gwr_result<- st_read("data/models/gwr_results_amsterdam.gpkg")
 
 gwr_result %>% 
   filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
@@ -19,6 +19,11 @@ gwr_result %>%
 gwr_result %>% 
   filter(living_area_TV < -1.96| living_area_TV > 1.96) %>% 
   mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96) %>% 
+  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
+
 
 
 

### 2023-04-03 1c. Data enrichment.R
ndvi

@@ -1,4 +1,4 @@
-easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse", "stars")
+easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse", "stars", "mapview")
 
 ############################################################ AMSTERDAM ###########################################################
 ############################################################ DATA ###########################################################
@@ -48,8 +48,16 @@ funda_data$ndvi100 <- ndvi100$NDVI_Amsterdam_100m.tif
 funda_data$ndvi300 <- ndvi300$NDVI_Amsterdam_300m.tif
 funda_data$ndvi500 <- ndvi500$NDVI_Amsterdam_500m.tif
 
+funda_data %>% 
+  mapview( zcol = "ndvi500", col.regions=brewer.pal(9, "YlOrRd"))
+
+
+
+
 #write results to updated gpkg
 st_write(funda_data, "data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+
 
 
 #read_sf("data/Noord_holland_polygon.shp") %>%

### 2023-04-03 3. Final analysis & Results.R

@@ -2,7 +2,7 @@ easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap")
 
 
 #Visualize results GWR model
-gwr_result<- st_read("data/models/gwr_results_amsterdam.gpkg")
+gwr_result<- st_read("data/models/mgwr_results_amsterdam_ndvi.gpkg")
 
 gwr_result %>% 
   filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
@@ -21,8 +21,8 @@ gwr_result %>%
   mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
-  filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96) %>% 
-  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
+  filter(ndvi100_TV < -1.96| ndvi100_TV > 1.96) %>% 
+  mapview( zcol = "ndvi100", col.regions=brewer.pal(9, "YlOrRd"))
 
 
 

### 2023-04-04 1c. Data enrichment.R
Update

@@ -3,15 +3,23 @@ easypackages::packages("sf", "sp", "osmdata", "FNN", "tidyverse", "stars", "mapv
 ############################################################ AMSTERDAM ###########################################################
 ############################################################ DATA ###########################################################
 funda_data <- st_transform(st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full.gpkg"), crs = 28992)
-amsterdam_boundaries <- st_transform(st_read("data/Amsterdam/PC4.json"), crs= 28992)
-
+amsterdam_boundaries <- st_read("data/Amsterdam/PC4.json")
 public_transport <- st_transform(st_read("data/Amsterdam/public_transport.json"), crs= 28992)
 tram <- public_transport %>% 
   filter(Modaliteit == "Tram")
 metro <- public_transport %>% 
   filter(Modaliteit == "Metro")
-
 train <- st_transform(st_read("data/Amsterdam/Stations_(NS).geojson"), crs= 28992)
+############################################################ OSM ###########################################################
+school <-  opq(st_bbox(amsterdam_boundaries)) %>%
+  add_osm_feature(key = "amenity", c("school")) %>%
+  osmdata_sf ()
+school_points <- st_as_sf (school$osm_points) %>% dplyr:: select(osm_id, amenity)
+
+daily_shops <-  opq(st_bbox(amsterdam_boundaries)) %>%
+  add_osm_feature(key = "shop", c("convenience", "department_store", "supermarket")) %>%
+  osmdata_sf ()
+daily_shops_points <- st_as_sf (daily_shops$osm_points) %>% dplyr:: select(osm_id, amenity)
 ############################################################ DISTANCES ######################################################
 nn_function <- function(measureFrom,measureTo,k) {
   measureFrom_Matrix <- as.matrix(measureFrom)
@@ -33,9 +41,26 @@ funda_data <- funda_data %>%
 funda_data <- funda_data %>%
   mutate(train_dist = nn_function(st_coordinates(funda_data$geom), st_coordinates(train$geometry), 1))
 
+#Re-project the point layer from WGS to local projection to have unit in meter
+school_points <-  st_transform (school_points, 28992)
+daily_shops_points <-  st_transform (daily_shops_points, 28992)
+
[…]

### 2023-04-04 Paper/paper.Rmd
Update

@@
 setwd("./..")
-funda_data <- st_read("data/funda_buy_28-03-2023_full_distances.gpkg")
+funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 setwd("Paper")
@@
 
-```{r test1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
-tm_shape(funda_data) +
-  tm_dots()
+```{r test1, echo=FALSE, fig.cap="Figure number", message=FALSE, warning=FALSE}
+#plot dependent variable
+# make some bbox magic 
+bbox_new <- st_bbox(PC4) # current bounding box 
+xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
+yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
+# bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
+bbox_new[3] <- bbox_new[3] + (0.35 * xrange) # xmax - right 
+# bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
+bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
+bbox_new <- bbox_new %>% # take the bounding box ... 
+  st_as_sfc() # ... and make it a sf polygon # looks better, does it?
+
+tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white")+
+  tm_shape(funda_data)+
+  tm_dots(c("ndvi500"), title = "NDVI (500m range)", size = 0.1) + 
+  tm_layout(title = "Amsterdam NDVI values",
+            #title.fontfamily = "cambria",
+            title.fontface = "bold",
+            #legend.text.fontfamily = "cambria",
+            #legend.title.fontfamily = "cambria",
+            legend.position = c("right", "top"),
+            legend.text.size = 0.75,
+            legend.title.size = 1)
 

### 2023-04-04 2a. OLS & SAC.R

@@ -1,19 +1,46 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync", "systemfonts")
 
 #load data
-funda_data <- st_read("data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
-#funda_data <- funda_data %>% filter(price <1000000)
 
 #plot dependent variable
-mapview(funda_data, zcol = "price", col.regions=brewer.pal(9, "YlOrRd"))
+# make some bbox magic 
+bbox_new <- st_bbox(PC4) # current bounding box 
+xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
+yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
+# bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
+bbox_new[3] <- bbox_new[3] + (0.35 * xrange) # xmax - right 
+# bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
+bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
+bbox_new <- bbox_new %>% # take the bounding box ... 
+  st_as_sfc() # ... and make it a sf polygon # looks better, does it? 
 
-tm_shape(PC4)+
-  tm_polygons()+
+tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white")+
 tm_shape(funda_data)+
-  tm_dots(c("price"), style = "log10_pretty") + 
-  tm_layout(legend.position = c("right", "top"), 
-            legend.text.size = 0.5, legend.title.size = 0.8)
+  tm_dots(c("price_m2"), title = "Price (m2)", breaks = c(0,1000,2500,5000,7500,10000,12500,15000,20000,30000), size = 0.1) + 
+  tm_layout(title = "Amsterdam house prices",
+            title.fontfamily = "cambria",
+            title.fontface = "bold",
+            legend.text.fontfamily = "cambria",
[…]

### 2023-04-04 3. Final analysis & Results.R
Update 3. Final analysis & Results.R

@@ -1,8 +1,12 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
 
 
 #Visualize results GWR model
-gwr_result<- st_read("data/models/mgwr_results_amsterdam_ndvi.gpkg")
+gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi_m2.gpkg")
+funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+funda_data %>% 
+  mapview( zcol = "price_m2", col.regions=brewer.pal(9, "YlOrRd"), at = seq(4000, 25000, 1000))
 
 gwr_result %>% 
   filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
@@ -16,16 +20,42 @@ gwr_result %>%
   filter(metro_dist_TV < -1.96| metro_dist_TV > 1.96) %>% 
   mapview( zcol = "metro_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
-gwr_result %>% 
-  filter(living_area_TV < -1.96| living_area_TV > 1.96) %>% 
-  mapview( zcol = "living_area", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
-  filter(ndvi100_TV < -1.96| ndvi100_TV > 1.96) %>% 
-  mapview( zcol = "ndvi100", col.regions=brewer.pal(9, "YlOrRd"))
+  filter(ndvi500_TV < -1.91| ndvi500_TV > 1.91) %>% 
+  mapview( zcol = "ndvi500", col.regions=brewer.pal(9, "YlOrRd"))
 
 
 
+gwr_result %>% 
+  filter(school_dist_TV < -1.91| school_dist_TV > 1.91) %>% 
+  mapview( zcol = "school_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(shops_dist_TV < -1.91| shops_dist_TV > 1.91) %>% 
+  mapview( zcol = "shops_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(centre_dist_TV < -1.91| centre_dist_TV > 1.91) %>% 
[…]

### 2023-04-04 2a. OLS & SAC.R
update

@@ -10,11 +10,33 @@ bbox_new <- st_bbox(PC4) # current bounding box
 xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
 yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
 # bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
-bbox_new[3] <- bbox_new[3] + (0.35 * xrange) # xmax - right 
+bbox_new[3] <- bbox_new[3] + (0.25 * xrange) # xmax - right 
 # bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
 bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
 bbox_new <- bbox_new %>% # take the bounding box ... 
   st_as_sfc() # ... and make it a sf polygon # looks better, does it? 
+
+library(stars)
+ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_100m.tif")
+
+
+tm_shape(ndvi, bbox = bbox_new)+
+  tm_raster() +
+  tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white", alpha = 0)+
+  tm_shape(funda_data)+
+  tm_dots(c("price_m2"), title = "Price (m2)", breaks = c(0,1000,2500,5000,7500,10000,12500,15000,20000,30000), size = 0.1) + 
+  tm_layout(title = "Amsterdam house prices",
+            title.fontfamily = "cambria",
+            title.fontface = "bold",
+            legend.text.fontfamily = "cambria",
+            legend.title.fontfamily = "cambria",
+            legend.position = c("right", "top"),
+            legend.text.size = 0.75,
+            legend.title.size = 1)
+
+
+
 
 tm_shape(PC4, bbox = bbox_new)+
   tm_polygons(col = "white")+

### 2023-04-04 3. Final analysis & Results.R

@@ -2,11 +2,11 @@ easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "sp
 
 
 #Visualize results GWR model
-gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi_m2.gpkg")
+gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
 
 funda_data %>% 
-  mapview( zcol = "price_m2", col.regions=brewer.pal(9, "YlOrRd"), at = seq(4000, 25000, 1000))
+  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
   filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
@@ -22,8 +22,8 @@ gwr_result %>%
 
 
 gwr_result %>% 
-  filter(ndvi500_TV < -1.91| ndvi500_TV > 1.91) %>% 
-  mapview( zcol = "ndvi500", col.regions=brewer.pal(9, "YlOrRd"))
+  filter(ndvi300_TV < -1.91| ndvi300_TV > 1.91) %>% 
+  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
 
 
 
@@ -47,7 +47,7 @@ gwr_result %>%
   mapview( zcol = "residual", col.regions=brewer.pal(9, "YlOrRd"))
 
 
-funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
+funda_KNN <- knearneigh(funda_data, k=50) #Identify k nearest neighbours for spatial weights 
 funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
 funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
 

### 2023-04-04 Paper/paper.Rmd

@@
 
+\maketitle
+
 # 1. Abstract
@@
 
-\begin{figure*}
+```{=latex}
+\begin{figure*}[ht]
   \centering
@@
 \end{figure*}
+
+```
+
+```{r eval=FALSE, include=FALSE}
+library(xtable)
+xtable(tail(mtcars))
+```
+
+```{=latex}
+\begin{table*}[ht]
+\centering
+\begin{tabular}{rrrrrrrrrrrr}
+  \hline
+ & mpg & cyl & disp & hp & drat & wt & qsec & vs & am & gear & carb \\ 
+  \hline
+Porsche 914-2 & 26.00 & 4.00 & 120.30 & 91.00 & 4.43 & 2.14 & 16.70 & 0.00 & 1.00 & 5.00 & 2.00 \\ 
+  Lotus Europa & 30.40 & 4.00 & 95.10 & 113.00 & 3.77 & 1.51 & 16.90 & 1.00 & 1.00 & 5.00 & 2.00 \\ 
+  Ford Pantera L & 15.80 & 8.00 & 351.00 & 264.00 & 4.22 & 3.17 & 14.50 & 0.00 & 1.00 & 5.00 & 4.00 \\ 
+  Ferrari Dino & 19.70 & 6.00 & 145.00 & 175.00 & 3.62 & 2.77 & 15.50 & 0.00 & 1.00 & 5.00 & 6.00 \\ 
+  Maserati Bora & 15.00 & 8.00 & 301.00 & 335.00 & 3.54 & 3.57 & 14.60 & 0.00 & 1.00 & 5.00 & 8.00 \\ 
+  Volvo 142E & 21.40 & 4.00 & 121.00 & 109.00 & 4.11 & 2.78 & 18.60 & 1.00 & 1.00 & 4.00 & 2.00 \\ 
+   \hline
+\end{tabular}
+\end{table*}
+
+```
 

### 2023-04-04 3. Final analysis & Results.R
update

@@ -26,7 +26,6 @@ gwr_result %>%
   mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
 
 
-
 gwr_result %>% 
   filter(school_dist_TV < -1.91| school_dist_TV > 1.91) %>% 
   mapview( zcol = "school_dist", col.regions=brewer.pal(9, "YlOrRd"))

### 2023-04-05 2a. OLS & SAC.R
Update

@@ -41,7 +41,7 @@ tm_shape(ndvi, bbox = bbox_new)+
 tm_shape(PC4, bbox = bbox_new)+
   tm_polygons(col = "white")+
 tm_shape(funda_data)+
-  tm_dots(c("price_m2"), title = "Price (m2)", breaks = c(0,1000,2500,5000,7500,10000,12500,15000,20000,30000), size = 0.1) + 
+  tm_dots(c("price_m2"), title = "Price (m2)", breaks = c(0,2500,5000,7500,10000,12500,15000,20000,30000), size = 0.1) + 
   tm_layout(title = "Amsterdam house prices",
             title.fontfamily = "cambria",
             title.fontface = "bold",
@@ -68,8 +68,8 @@ tm_shape(PC4, bbox = bbox_new)+
 funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
 funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
 funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
-mc_global_knn <- moran.mc(funda_data$price, funda_KNN_w, 2999, alternative="greater")
-plot(mc_global_knn)
+mc_global_knn <- moran.mc(funda_data$price_m2, funda_KNN_w, 2999, alternative="greater")
+plot(mc_global_knn, xlab = "Dependent variable (price m2)")
 mc_global_knn
 #there is significant spatial autocorrelation
 
@@ -86,7 +86,8 @@ plot(model)
 #test spatial autocorrelation in residuals
 mc_global_OLS <- moran.mc(model$residuals, funda_KNN_w, 2999, zero.policy= TRUE, alternative="greater")
 #plot the  Moran's I
-plot(mc_global_OLS)
+par(mfrow=c(1,1))
+plot(mc_global_OLS, xlab = "Residuals of OLS model")
 mc_global_OLS
 
 funda_data$res_lm <- model$residuals
@@ -98,7 +99,7 @@ sac_model = sacsarlm(equation, data = funda_data, listw= funda_KNN_w, zero.polic
 summary(sac_model, Nagelkerke=T)
 #check residual autocorrelation
 mc2_global_sac <-moran.mc(sac_model$residuals, funda_KNN_w, 2999, alternative="greater")
-plot(mc2_global_sac)
[…]

### 2023-04-05 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -73,7 +73,7 @@ plot(mc_global_knn, xlab = "Dependent variable (price m2)")
 mc_global_knn
 #there is significant spatial autocorrelation
 
-equation <- price_m2 ~ bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi500 + centre_dist + zuid_dist + shops_dist + school_dist
+equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi500 + centre_dist + zuid_dist + shops_dist + school_dist
 #OLS
 model <- lm(equation, 
             data = funda_data)

### 2023-04-05 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -54,7 +54,7 @@ tm_shape(funda_data)+
 tm_shape(PC4, bbox = bbox_new)+
   tm_polygons(col = "white")+
   tm_shape(funda_data)+
-  tm_dots(c("ndvi500"), title = "NDVI (500m range)", size = 0.1) + 
+  tm_dots(c("ndvi300"), title = "NDVI (300m range)", size = 0.1) + 
   tm_layout(title = "Amsterdam NDVI values",
             title.fontfamily = "cambria",
             title.fontface = "bold",
@@ -73,7 +73,7 @@ plot(mc_global_knn, xlab = "Dependent variable (price m2)")
 mc_global_knn
 #there is significant spatial autocorrelation
 
-equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi500 + centre_dist + zuid_dist + shops_dist + school_dist
+equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi300 + centre_dist + zuid_dist + shops_dist + school_dist
 #OLS
 model <- lm(equation, 
             data = funda_data)

### 2023-04-05 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -5,7 +5,7 @@ funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_dist
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 
 #plot dependent variable
-# make some bbox magic 
+# Extend bbox for plots
 bbox_new <- st_bbox(PC4) # current bounding box 
 xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
 yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
@@ -13,8 +13,8 @@ yrange <- bbox_new$ymax - bbox_new$ymin # range of y values
 bbox_new[3] <- bbox_new[3] + (0.25 * xrange) # xmax - right 
 # bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
 bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
-bbox_new <- bbox_new %>% # take the bounding box ... 
-  st_as_sfc() # ... and make it a sf polygon # looks better, does it? 
+bbox_new <- bbox_new %>%
+  st_as_sfc() 
 
 library(stars)
 ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_100m.tif")
@@ -69,11 +69,12 @@ funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spat
 funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
 funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
 mc_global_knn <- moran.mc(funda_data$price_m2, funda_KNN_w, 2999, alternative="greater")
-plot(mc_global_knn, xlab = "Dependent variable (price m2)")
+plot(mc_global_knn, xlab = "Dependent variable (price per squared meter)")
 mc_global_knn
 #there is significant spatial autocorrelation
 
 equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi300 + centre_dist + zuid_dist + shops_dist + school_dist
+
 #OLS
 model <- lm(equation, 
             data = funda_data)
@@ -90,10 +91,6 @@ par(mfrow=c(1,1))
 plot(mc_global_OLS, xlab = "Residuals of OLS model")
[…]

### 2023-04-05 Paper/paper.Rmd
update

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)
+knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
 
@@
 ```{=latex}
-\begin{figure*}[ht]
+\begin{figure}[ht]
   \centering
-  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
+  \includegraphics[width=\linewidth]{figures/raster.png}
   \caption{This is a figure.}
-\end{figure*}
+\end{figure}
 
@@
 <div id="refs"></div>
+
+# Script 1
+
+```{r eval = FALSE}
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
+
+#Visualize results GWR model
+gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
+funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+funda_data %>% 
+  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
+  mapview( zcol = "tram_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(train_dist_TV < -1.96| train_dist_TV > 1.96) %>% 
+  mapview( zcol = "train_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(metro_dist_TV < -1.96| metro_dist_TV > 1.96) %>% 
+  mapview( zcol = "metro_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(ndvi300_TV < -1.91| ndvi300_TV > 1.91) %>% 
+  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(school_dist_TV < -1.91| school_dist_TV > 1.91) %>% 
+  mapview( zcol = "school_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(shops_dist_TV < -1.91| shops_dist_TV > 1.91) %>% 
+  mapview( zcol = "shops_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(centre_dist_TV < -1.91| centre_dist_TV > 1.91) %>% 
+  mapview( zcol = "centre_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  filter(zuid_dist_TV < -1.91| zuid_dist_TV > 1.91) %>% 
+  mapview( zcol = "zuid_dist", col.regions=brewer.pal(9, "YlOrRd"))
+
+gwr_result %>% 
+  mapview( zcol = "residual", col.regions=brewer.pal(9, "YlOrRd"))
+
+funda_KNN <- knearneigh(funda_data, k=50) #Identify k nearest neighbours for spatial weights 
+funda_nbq_KNN <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object
+funda_KNN_w <- nb2listw(funda_nbq_KNN, style="W", zero.policy = TRUE)
+
+mc_gwr <- moran.mc(gwr_result$residual, funda_KNN_w, 2999, zero.policy= TRUE, alternative="greater")
+mc_gwr
+plot(mc_gwr)
+funda_data %>% 
+  ggplot(aes(y = price_m2, x = metro_dist)) + geom_point()
+
+map <- mapview(gwr_result, zcol = "metro", col.regions=brewer.pal(9, "YlOrRd"))
+
+map
+
+gwr_result %>% 
+  ggplot(aes(x = residual)) + geom_density()
+
+funda_data <- st_read("data/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
+
+tm_shape(PC4)+
+  tm_polygons()+
+  tm_shape(gwr_result)+
+  tm_dots(c("train_dist")) + 
+  tm_layout(legend.position = c("right", "top"), 
+            legend.text.size = 0.5, legend.title.size = 0.8)
+
+```

### 2023-04-05 1a. Pre-processing.R

@@ -1,16 +1,16 @@
-###Important to specify correct names for the original data and the desination data
+###Important to specify correct names for the original data and the destination data
 
 
 easypackages::packages("raster", "sf", "tidyverse", "tidygeocoder", "mapview")
 #paths
 origin_path <- "Scraper/data/"
-desination_path <-  "data/Houseprices"
+destination_path <-  "data/Houseprices/"
 
 #below names need to be specified
 
 orgin_df_name <- "funda_buy_amsterdam_31-03-2023_full.csv"
-desination_df_name <- "funda_buy_amsterdam_31-03-2023_fulllatlon.csv"
-desination_gpkg_name <- "funda_buy_amsterdam_31-03-2023_full.gpkg"
+destination_df_name <- "funda_buy_amsterdam_31-03-2023_fulllatlon.csv"
+destination_gpkg_name <- "funda_buy_amsterdam_31-03-2023_full.gpkg"
 
 #load raw scraped Funda data from the folder
 
@@ -38,7 +38,7 @@ df_geo <- df %>%
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
 
 #wire to csv
-write.csv(df_geo, paste0(desination_path, desination_df_name))
+write.csv(df_geo, paste0(destination_path, destination_df_name))
 
 #write to geopackage 
 
@@ -56,8 +56,14 @@ df_spatial_clipped <- st_intersection(df_spatial, st_transform(st_read("data/Ams
 #view data
 mapview(df_spatial_clipped)
 
+#adjust for faulty house age values
+
+df_spatial_clipped <- df_spatial_clipped %>% 
+  mutate(house_age = ifelse(house_age == 2023, NA, house_age),
+         house_age = ifelse(is.na(house_age), mean(house_age, na.rm = T), house_age))
+
 #write to geopackage
-st_write(df_spatial_clipped,paste0(desination_path, desination_gpkg_name))
+st_write(df_spatial_clipped,paste0(destination_path, destination_gpkg_name))
 
 
 

### 2023-04-05 1c. Data enrichment.R

@@ -74,4 +74,5 @@ funda_data$ndvi300 <- ndvi300$NDVI_Amsterdam_300m.tif
 funda_data$ndvi500 <- ndvi500$NDVI_Amsterdam_500m.tif
 
 #write results to updated gpkg
+
 st_write(funda_data, "data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")

### 2023-04-05 3. Final analysis & Results.R

@@ -1,9 +1,15 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
 
 
+
+
 #Visualize results GWR model
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+
+mean(funda_data$shops_dist)
+sd(funda_data$shops_dist)
+
 
 funda_data %>% 
   mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
@@ -22,24 +28,24 @@ gwr_result %>%
 
 
 gwr_result %>% 
-  filter(ndvi300_TV < -1.91| ndvi300_TV > 1.91) %>% 
+  filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96) %>% 
   mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
 
 
 gwr_result %>% 
-  filter(school_dist_TV < -1.91| school_dist_TV > 1.91) %>% 
+  filter(school_dist_TV < -1.96| school_dist_TV > 1.96) %>% 
   mapview( zcol = "school_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
-  filter(shops_dist_TV < -1.91| shops_dist_TV > 1.91) %>% 
+  filter(shops_dist_TV < -1.96| shops_dist_TV > 1.96) %>% 
   mapview( zcol = "shops_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
-  filter(centre_dist_TV < -1.91| centre_dist_TV > 1.91) %>% 
+  filter(centre_dist_TV < -1.96| centre_dist_TV > 1.96) %>% 
   mapview( zcol = "centre_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
-  filter(zuid_dist_TV < -1.91| zuid_dist_TV > 1.91) %>% 
+  filter(zuid_dist_TV < -1.96| zuid_dist_TV > 1.96) %>% 
   mapview( zcol = "zuid_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
 gwr_result %>% 
@@ -72,3 +78,34 @@ tm_shape(PC4)+
[…]

### 2023-04-05 Yúri/osm_data.R

@@ -1,109 +1,0 @@
-easypackages::packages("sf", "sp", "osmdata", "FNN")
-library(dplyr)
-
-#read_sf("data/Noord_holland_polygon.shp") %>%
- # st_transform(crs=4326) %>%
-  #st_write("Noord_Holland.gpkg", )
-
-# POIs: school, university, hospital/clinic, shopping center/mall, train, subway, bus, supermarket/market
-
-province_boundaries <- st_read ("data/Noord_Holland.gpkg")
-funda_data <- st_read ("data/funda_buy_28-03-2023_full.gpkg")
-
-# Get OSM data
-bus <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "amenity", c("bus_station")) %>%
-  osmdata_sf ()
-bus_points <- st_as_sf (bus$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-
-subway <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "railway", c("subway_entrance")) %>%
-  osmdata_sf ()
-subway_points <- st_as_sf (subway$osm_points) %>% dplyr:: select(osm_id)
-
-
-train <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "building", c("train_station")) %>%
-  osmdata_sf ()
-train_points <- st_as_sf (train$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-university <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "amenity", c("university")) %>%
-  osmdata_sf ()
-university_points <- st_as_sf (university$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-school <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "amenity", c("school")) %>%
-  osmdata_sf ()
-school_points <- st_as_sf (school$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-hospital <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "amenity", c("hospital")) %>%
-  osmdata_sf ()
-hospital_points <- st_as_sf (hospital$osm_points) %>% dplyr:: select(osm_id, amenity)
-
-mall <-  opq(st_bbox(province_boundaries)) %>%
-  add_osm_feature(key = "shop", c("mall")) %>%
[…]

### 2023-04-05 2a. OLS & SAC.R
update

@@ -1,8 +1,10 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync", "systemfonts")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "car", "spdep", "spatialreg", "leafsync", "systemfonts", "stars")
 
 #load data
 funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
+ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
+
 
 #plot dependent variable
 # Extend bbox for plots
@@ -16,14 +18,54 @@ bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top
 bbox_new <- bbox_new %>%
   st_as_sfc() 
 
-library(stars)
-ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_100m.tif")
+
+
+
+ndvi_plot <- tm_shape(ndvi, bbox = bbox_new)+
+  tm_raster(palette = "YlGn", title = "NDVI value") +
+  tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white", alpha = 0, border.col = "black")+
+  tm_layout(title = "Amsterdam NDVI values with 300m range",
+            title.fontfamily = "cambria",
+            title.fontface = "bold",
+            legend.text.fontfamily = "cambria",
+            legend.title.fontfamily = "cambria",
+            legend.position = c("right", "top"),
+            legend.text.size = 0.75,
+            legend.title.size = 1)
+
+houseprices_plot <- tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white", border.col = "black")+
+  tm_shape(funda_data)+
+  tm_dots(c("price_m2"), title = "Price (m2)", 
+          breaks = c(0,2500,5000,7500,10000,12500,15000,20000,30000),
+          size = 0.1) + 
+  tm_layout(title = "Amsterdam house prices",
+            title.fontfamily = "cambria",
+            title.fontface = "bold",
+            legend.text.fontfamily = "cambria",
+            legend.title.fontfamily = "cambria",
[…]

### 2023-04-05 3. Final analysis & Results.R

@@ -94,13 +94,16 @@ bw_df %>%
 
 #################### create coef plot for ndvi
 
+library(RColorBrewer)
+my_palette <- terrain.colors(10)[3:9]
+
 
 tm_shape(PC4, bbox = bbox_new)+
-  tm_polygons(col = "white", alpha = 0)+
+  tm_polygons(col = "white", alpha = 0, border.col = "Black")+
   tm_shape(gwr_result %>%  filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96))+
-  tm_dots(c("ndvi300"), title = "Price (m2)", size = 0.1) + 
-  tm_layout(title = "Amsterdam house prices",
-            title.fontfamily = "cambria",
+  tm_dots(c("ndvi300"), title = "Coefficient", size = 0.1) + 
+  tm_layout(title = "Significant (95%) NDVI coefficients GWR model",
+            title.fontfamily = "Cambria",
             title.fontface = "bold",
             legend.text.fontfamily = "cambria",
             legend.title.fontfamily = "cambria",

### 2023-04-05 2a. OLS & SAC.R
Update 2a. OLS & SAC.R

@@ -6,7 +6,7 @@ PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
 
 
-#plot dependent variable
+#plot variables of interest
 # Extend bbox for plots
 bbox_new <- st_bbox(PC4) # current bounding box 
 xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
@@ -17,9 +17,6 @@ bbox_new[3] <- bbox_new[3] + (0.25 * xrange) # xmax - right
 bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
 bbox_new <- bbox_new %>%
   st_as_sfc() 
-
-
-
 
 ndvi_plot <- tm_shape(ndvi, bbox = bbox_new)+
   tm_raster(palette = "YlGn", title = "NDVI value") +
@@ -51,53 +48,10 @@ houseprices_plot <- tm_shape(PC4, bbox = bbox_new)+
 
 tmap_arrange(ndvi_plot,houseprices_plot, asp = NULL, ncol = 2)
 
-
-
-
-
-
-
-
-
-
-
-
-tm_shape(ndvi, bbox = bbox_new)+
-  tm_raster(palette = "YlGn") +
-  tm_shape(PC4, bbox = bbox_new)+
-  tm_polygons(col = "white", alpha = 0, border.col = "black")+
-  tm_shape(funda_data)+
-  tm_dots(c("price_m2"), title = "Price (m2)", breaks = c(0,1000,2500,5000,7500,10000,12500,15000,20000,30000), size = 0.1) + 
-  tm_layout(title = "Amsterdam house prices",
-            title.fontfamily = "cambria",
-            title.fontface = "bold",
-            legend.text.fontfamily = "cambria",
-            legend.title.fontfamily = "cambria",
-            legend.position = c("right", "top"),
-            legend.text.size = 0.75,
-            legend.title.size = 1)
-
-
-
-
-
-tm_shape(PC4, bbox = bbox_new)+
-  tm_polygons(col = "white")+
-  tm_shape(funda_data)+
-  tm_dots(c("ndvi300"), title = "NDVI (300m range)", size = 0.1) + 
-  tm_layout(title = "Amsterdam NDVI values",
-            title.fontfamily = "cambria",
-            title.fontface = "bold",
-            legend.text.fontfamily = "cambria",
[…]

### 2023-04-06 1a. Pre-processing.R
Update

@@ -1,19 +1,17 @@
 ###Important to specify correct names for the original data and the destination data
 
-
 easypackages::packages("raster", "sf", "tidyverse", "tidygeocoder", "mapview")
+
 #paths
 origin_path <- "Scraper/data/"
 destination_path <-  "data/Houseprices/"
 
 #below names need to be specified
-
 orgin_df_name <- "funda_buy_amsterdam_31-03-2023_full.csv"
 destination_df_name <- "funda_buy_amsterdam_31-03-2023_fulllatlon.csv"
 destination_gpkg_name <- "funda_buy_amsterdam_31-03-2023_full.gpkg"
 
 #load raw scraped Funda data from the folder
-
 df <- read.csv(paste0(origin_path, orgin_df_name))
 
 #show and adjust structure
@@ -28,7 +26,6 @@ str(df)
 
 #create correct address-line based on the funda data
 #geocode the addres line with OSM to lat long columns
-
 df_geo <- df %>% 
   separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4", "optional5"), " ") %>% 
   mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4, optional5),
@@ -37,27 +34,23 @@ df_geo <- df %>%
   select(-optional1, -optional2, -optional3, -optional4, -optional5) %>% 
   geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
 
-#wire to csv
+#write to csv
 write.csv(df_geo, paste0(destination_path, destination_df_name))
 
-#write to geopackage 
-
-#NAs will be dropped and the data will be clipped to Noord-Holland to delete any falsely geocoded locations.
-
+#NAs will be dropped and the data will be clipped to Amsterdam to delete any falsely geocoded locations.
 df_geo_clean <- df_geo %>% drop_na() 
 
 df_spatial = st_as_sf(df_geo_clean, coords = c( "longitude", "latitude"), crs = 4326)
 #transform to RDNEW
 df_spatial <- st_transform(df_spatial, crs = 28992)
 
-#clip data bases on NH boundary
+#clip data basesd on Amsterdam PC4 boundaries
 df_spatial_clipped <- st_intersection(df_spatial, st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992))
 
 #view data
 mapview(df_spatial_clipped)
 
 #adjust for faulty house age values
-
[…]

### 2023-04-06 3. Final analysis & Results.R

@@ -1,15 +1,8 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
 
-
-
-
 #Visualize results GWR model
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
-
-mean(funda_data$shops_dist)
-sd(funda_data$shops_dist)
-
 
 funda_data %>% 
   mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
@@ -26,11 +19,9 @@ gwr_result %>%
   filter(metro_dist_TV < -1.96| metro_dist_TV > 1.96) %>% 
   mapview( zcol = "metro_dist", col.regions=brewer.pal(9, "YlOrRd"))
 
-
 gwr_result %>% 
   filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96) %>% 
   mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
-
 
 gwr_result %>% 
   filter(school_dist_TV < -1.96| school_dist_TV > 1.96) %>% 

### 2023-04-06 3. Final analysis & Results.R
update

@@ -1,102 +1,23 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
 
-
-
-
 #Visualize results GWR model
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
-funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
-
-mean(funda_data$shops_dist)
-sd(funda_data$shops_dist)
-
-
-funda_data %>% 
-  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(tram_dist_TV < -1.96| tram_dist_TV > 1.96) %>% 
-  mapview( zcol = "tram_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(train_dist_TV < -1.96| train_dist_TV > 1.96) %>% 
-  mapview( zcol = "train_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(metro_dist_TV < -1.96| metro_dist_TV > 1.96) %>% 
-  mapview( zcol = "metro_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-
-gwr_result %>% 
-  filter(ndvi300_TV < -1.96| ndvi300_TV > 1.96) %>% 
-  mapview( zcol = "ndvi300", col.regions=brewer.pal(9, "YlOrRd"))
-
-
-gwr_result %>% 
-  filter(school_dist_TV < -1.96| school_dist_TV > 1.96) %>% 
-  mapview( zcol = "school_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(shops_dist_TV < -1.96| shops_dist_TV > 1.96) %>% 
-  mapview( zcol = "shops_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(centre_dist_TV < -1.96| centre_dist_TV > 1.96) %>% 
-  mapview( zcol = "centre_dist", col.regions=brewer.pal(9, "YlOrRd"))
-
-gwr_result %>% 
-  filter(zuid_dist_TV < -1.96| zuid_dist_TV > 1.96) %>% 
[…]

### 2023-04-06 Paper/paper.Rmd
paper update

--- 2023-04-04 Paper/paper.Rmd
@@
 ---
-title: "Explaining Noord-Holland house prices"
+title: "Estimating the Effect of Urban Green Spaces on Residential House Prices in Amsterdam"
+subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression" 
 author: 
@@
     pdf_document:
+        extra_dependencies: ["float", "booktabs"]
         latex_engine: xelatex
+        pandoc_args: [
+      "-V", "classoption=twocolumn"
+    ]
+
+subparagraph: yes
+header-includes: |
+  \usepackage{titlesec}
+  \titlespacing{\section}{0pt}{10pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+  \titlespacing{\subsection}{0pt}{4pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+  \titlespacing{\subsubsection}{0pt}{5pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
 mainfont: Cambria
-classoption:
-- twocolumn
 bibliography: references.bib
 csl: apa.csl
+
 ---
@@
 ```{r include=FALSE}
+#all code for plots
 library(mapview)
@@
 
-# 1. Abstract
-In an effort to create a green and diversified energy system, the Dutch national government aims to stimulate the adoption of renewables.
-In this context, wind energy is considered to be one of the most promising.
-However, the potential of this type of renewable is greatly influenced by existing land-use claims and related spatial and social policies.
-It becomes clear that, shifting to wind energy as a renewable energy source is a key challenge in densely populated countries, such as the Netherlands.
-Therefore, this study aims to examine the energy potential of suitable onshore wind farm sites in the province of North-Holland.
-In order to identify suitable areas for the placement of wind turbines, several spatial and social criteria and constraints were considered in three scenarios using a multi-criteria decision analysis method.
-Based on a power density function, the total energy potential of the suitable areas was determined.
-The results of the scenarios ranged from 2 MW to 3017 MW of prospective energy generable.
-These large ranges of potential show the significant impact of constraints and criteria and underline the need for a comprehensive understanding of the relationship between site suitability and spatial policies and choices.
+# 1. Introduction
+Green spaces play an important role in urban ecosystems.
+As a natural purifier for cities, these areas help control soil erosion [1], improve air quality [2, 3], reduce the urban heat island effect [4–6] and are considered to be aesthetically pleasing [7].
+Moreover, green areas in cities are shown to provide notable improvements in residents’ physical and mental wellbeing [8, 9].
+As the benefits of greenness in urban areas are increasingly recognised, numerous cities have developed urban greening programs to expand parks, build green roofs or plant more trees [10–12].
+However, evaluating the effects of these initiatives to justify their costs remains a challenge, partly due to data sparsity.
 
-Plot in text
+A review of literature revealed that there are several studies that aimed to examine the effect of urban green spaces on residential house prices [13–19].
+Often these studies adopted a hedonic pricing approach to estimate the economic value that individuals place on particular property characteristics, as reflected in the real-estate prices [14, 15].
+However, most literature only focused on the distance to urban green areas as a valuation indicator [20, 21].
+Here, a few studies considered a more comprehensive appreciation of greenness in cities by employing vegetation indices and the interaction with property and public amenities [16, 17, 22, 23].
 
-```{r test3, message=FALSE, warning=FALSE, include=FALSE}
-pdf("figures/plot.pdf")
-tm_shape(funda_data) +
-  tm_dots(c("price", "living_area"))
-dev.off()
+Among the literature that explored the property value premium of urban green spaces more exhaustive, most adopted the normalised difference vegetation index (NDVI) [16, 22, 23].
+Here, the relative abundance of vegetation was measured across varying buffer distances using remote sensing systems with various spatial resolutions.
+Moreover, most of these studies also considered the interaction with residential and public amenities, such as the number of rooms or proximity to convenience stores [16, 23].
+However, these analyses were mainly performed in cities with conservative urban greening programs in place [23].
+Lastly, the adoption of NDVI for identifying (urban) green spaces is often criticised due to its sensitivity to varying spatial scales and inability to differentiate between vegetation types [24].
+Nonetheless, the index is widely accepted and can be considered almost a standard approach [25, 26].
+
+Based on the examined literature, a hedonic pricing approach in combination with the normalised difference vegetation index and the interaction with particular amenities emerges as an effective method to estimate the effect of urban green spaces on residential house prices.
+Given the limited literature available on property value premiums associated with greenness exposure in cities with more progressive urban greening programs, this study aims to answer the research question of what the economic value of urban green spaces in the city of Amsterdam is in the year 2023, as reflected in the real-estate prices.
+
+# 2. Methods
+## 2.1 Study Area
+The geographical scope in this study concentrated on the city of Amsterdam, as presented in Figure 1.
+The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27] that occupy a space of 219.3 km2  [28].
+As a result, the city is considered one of the most densely populated in the country.
+Surrounding the residential areas, the vast majority of land is occupied with vegetation [29].
+Moreover, the municipality has progressive urban greening programs in place, stimulating and obligating residents and city districts to participate in greening initiatives [12].
+As a result, these policies aimed at expanding urban green spaces have the potential to increase nearby housing premiums.
+
+```{=latex}
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\linewidth]{figures/study_area.png}
+  \caption{Overview of the study area.}
+\end{figure}
 ```
 
-\begin{figure*}
+## 2.2 Data
+In this study, property listings were obtained from Funda.nl, a Dutch online real-estate platform [30].
+Here, data included the sale price and property characteristics of residential houses in Amsterdam listed on the platform on 31 March 2023.
+Moreover, information about multiple public amenities in Amsterdam were obtained from a variety of sources, including ArcGIS [31], OpenStreetMap.org [32, 33] and the municipality of Amsterdam [34].
+Selection of public amenities, used as controlling variables, were based on applicable literature, as presented in Table 1.
+Adjusting for these variables was done to limit the effect of potential confounders on the association of interest.
+Finally, remote sensing images in red and near-infrared were obtained from Sentinel-2 in August 2022 [35].
+This allowed on the capitalisation of high greenness levels in that period, leading to improved differentiation between green and urban areas.
+
+## 2.3 Data Enrichment
+
+```{=latex}
+\begin{figure}[t]
   \centering
-  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
+  \includegraphics[width=\linewidth]{figures/raster5.png}
+  \caption{Illustrative figrue of the focal statistics as buffer distance.}
+\end{figure}
+```
+## 2.4 Analysis
+
+```{=latex}
+\begin{table}[]
+\centering
+\caption{Included variables}
+\begin{tabular}{@{}lll@{}}
+\toprule
+Variable            & Mean (n = 1719) & SD \\ \midrule
+Living area (m2)    & 105.7           & 71.0               \\
+Bedroom (N)         & 2.5             & 1.4                \\
+Bathroom (N)        & 1.1             & 0.7                \\
+House age (Years)   & 76.9            & 63.2               \\
+Train distance (m)  & 1703.7          & 958.2              \\
+Metro distance (m)  & 1303.2          & 951.8              \\
+Tram distance (m)   & 689.1           & 1024.7             \\
+NDVI 300m range     & 0.212           & 0.069              \\
+Centre distance (m) & 3770.5          & 2288.1             \\
+Zuid distance (m)   & 4659.2          & 2228.3             \\
+School distance (m) & 268.3           & 183.8              \\
+Shops distance (m)  & 266.7           & 206.9              \\
+                    &                 &                    \\ \bottomrule
+
+\end{tabular}
+\end{table}
+```
+
+## 2.4.1 Ordinary Least Squares
+
+## 2.4.2 Spatial Dependence and Heterogeineity
+
+## 2.4.3 Geographically Weighted Regression
+
+# 3. Results and Discussion
+
+```{=latex}
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\linewidth]{figures/ndvi_houseprices.png}
   \caption{This is a figure.}
 \end{figure*}
-
-# 2. Introduction
-One of the aims of the Dutch national government is to stimulate renewables in order to create a green and diversified energy system [1].
-Among the several alternatives available, wind energy is considered to be one of the most promising due to its limited environmental impact and economic viability [2].
-Despite the advantages, wind energy still plays a marginal role in the total Dutch energy consumption [3].
-While various reasons can be identified, this small share mainly relates to the fact that wind energy has to compete with other spatial claims that may be deemed more important.
-
-Under the current legal framework, provinces are largely responsible for shaping spatial and energy plans [4].
-However, the allocation for this type of renewable poses significant challenges.
-Apart from technical and physical incompatibility that influences the onshore location of wind farms, societal and environmental considerations are similarly important.
-Nature and other valuable landscapes often have a protected status, limiting or at least constraining the allocation of wind farms [5].
-Moreover, societal resistance to environmental impact experienced by those near wind turbines also inspire spatial energy policies and choices [6].
-As a result, the transition to onshore wind turbines as a source of renewable energy represents a key challenge in a country that is as densely populated as the Netherlands.
-
-A review of literature revealed that there is a multitude of studies that aimed to identify the spatial potential for wind energy deployment.
-Often studies applied geospatial information systems in combination with a multi-criteria decision analysis to examine the suitability of sites [2, 7].
-Here, areas of interest were evaluated based on a variety of criteria and constraints.
-In general, these studies employed a rule-based approach considering mostly physical [8], economic [9, 10] and environmental [2] aspects with only a few placing emphasis on social considerations [11, 12].
-Moreover, the literature revealed that studies using a scenario-based approach were limited, especially in the Netherlands [13].
-As a result, a comprehensive understanding of the relationship between site suitability for wind farms and multiple spatial policies and choices remain underdeveloped.
-
-In an effort to examine the energy potential of sites suitable for the production of wind energy, mathematical functions are the main tools used in literature [14].
-Among the several types available, wind power density is most commonly employed [15–17].
-Although several studies have proven its limitations in wind energy assessment due to its flexibility and simplicity, the method is widely accepted and can be considered almost a standard approach [18, 19].
-
-Based on the examined literature, multi-criteria decision analysis in combination with a wind power density function emerges as an effective tool for assessing the energy potential of sites suitable for the production of wind energy.
-Given the limited literature available on wind farm allocation in the Netherlands and the evident challenges associated with balancing elements of interest, this study aims to provide a preliminary overview of the energy potential of suitable onshore wind farm sites in the province of North-Holland.
-
-# 3. Methods
-## 3.1 Study Area
-In this study, the geographical scope was limited to the province of North-Holland, as presented in Figure 1.
-The area is situated in the North-Western part of the Netherlands and occupies an onshore space of 2,840 km2 [5].
-The province is home to almost 2,8 million inhabitants, making it one of the most densely populated regions in the country (684 inhabitants/km2) [20].
-Outside the large urban areas, the vast majority of the land is agricultural with two areas designated as National Parks [20, 21].
-At the moment, the province is obligated by the Dutch national government to have an extra installed onshore wind capacity of 105.5 MW [4, 5].
-
-Plot klein
-
-```{r test1, echo=FALSE, fig.cap="Figure number", message=FALSE, warning=FALSE}
-#plot dependent variable
-# make some bbox magic 
-bbox_new <- st_bbox(PC4) # current bounding box 
-xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
-yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
-# bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
-bbox_new[3] <- bbox_new[3] + (0.35 * xrange) # xmax - right 
-# bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
-bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
-bbox_new <- bbox_new %>% # take the bounding box ... 
-  st_as_sfc() # ... and make it a sf polygon # looks better, does it?
-
-tm_shape(PC4, bbox = bbox_new)+
-  tm_polygons(col = "white")+
-  tm_shape(funda_data)+
-  tm_dots(c("ndvi500"), title = "NDVI (500m range)", size = 0.1) + 
-  tm_layout(title = "Amsterdam NDVI values",
-            #title.fontfamily = "cambria",
-            title.fontface = "bold",
-            #legend.text.fontfamily = "cambria",
-            #legend.title.fontfamily = "cambria",
-            legend.position = c("right", "top"),
-            legend.text.size = 0.75,
-            legend.title.size = 1)
-
 ```
 
-```{r foo, out.width="100%", fig.cap="An example image.", include=FALSE, echo=FALSE}
-knitr::include_graphics("figures/plot.pdf")
-```
+# 4. Conclusion
 
-\onecolumn
-of plot groot
-
-```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Plot of NH full page"}
-tm_shape(funda_data) +
-  tm_dots()
-```
-
-Bron vermelding zo:
-@fotheringham2017multiscale
-
-Of zo:
-[-@fotheringham2017multiscale]
-
-# References
-
-<div id="refs"></div>
+# 5. References

### 2023-04-06 README.Rmd
update readme

@@
 Yúri Grings [Linkedin](https://www.linkedin.com/in/yurigrings/), Thomas Nibbering [Linkedin](https://www.linkedin.com/in/thomas-nibbering/), Jitse Ruurd Nauta [Linkedin](https://www.linkedin.com/in/jitseruurdnauta/)
+
+# Paper
+
+## Introduction
+
+Green spaces play an important role in urban ecosystems.
+As a natural purifier for cities, these areas help control soil erosion [1], improve air quality [2, 3], reduce the urban heat island effect [4–6] and are considered to be aesthetically pleasing [7].
+Moreover, green areas in cities are shown to provide notable improvements in residents’ physical and mental wellbeing [8, 9].
+As the benefits of greenness in urban areas are increasingly recognised, numerous cities have developed urban greening programs to expand parks, build green roofs or plant more trees [10–12].
+However, evaluating the effects of these initiatives to justify their costs remains a challenge, partly due to data sparsity.
+
+A review of literature revealed that there are several studies that aimed to examine the effect of urban green spaces on residential house prices [13–19].
+Often these studies adopted a hedonic pricing approach to estimate the economic value that individuals place on particular property characteristics, as reflected in the real-estate prices [14, 15].
+However, most literature only focused on the distance to urban green areas as a valuation indicator [20, 21].
+Here, a few studies considered a more comprehensive appreciation of greenness in cities by employing vegetation indices and the interaction with property and public amenities [16, 17, 22, 23].
+
+Among the literature that explored the property value premium of urban green spaces more exhaustive, most adopted the normalised difference vegetation index (NDVI) [16, 22, 23].
+Here, the relative abundance of vegetation was measured across varying buffer distances using remote sensing systems with various spatial resolutions.
+Moreover, most of these studies also considered the interaction with residential and public amenities, such as the number of rooms or proximity to convenience stores [16, 23].
+However, these analyses were mainly performed in cities with conservative urban greening programs in place [23].
+Lastly, the adoption of NDVI for identifying (urban) green spaces is often criticised due to its sensitivity to varying spatial scales and inability to differentiate between vegetation types [24].
+Nonetheless, the index is widely accepted and can be considered almost a standard approach [25, 26].
+
+Based on the examined literature, a hedonic pricing approach in combination with the normalised difference vegetation index and the interaction with particular amenities emerges as an effective method to estimate the effect of urban green spaces on residential house prices.
+Given the limited literature available on property value premiums associated with greenness exposure in cities with more progressive urban greening programs, this study aims to answer the research question of what the economic value of urban green spaces in the city of Amsterdam is in the year 2023, as reflected in the real-estate prices.
+
+## Methods
+
+### Study Area
+
+The geographical scope in this study concentrated on the city of Amsterdam, as presented in Figure 1.
+The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27] that occupy a space of 219.3 km2  [28].
+As a result, the city is considered one of the most densely populated in the country.
+Surrounding the residential areas, the vast majority of land is occupied with vegetation [29].
+Moreover, the municipality has progressive urban greening programs in place, stimulating and obligating residents and city districts to participate in greening initiatives [12].
+As a result, these policies aimed at expanding urban green spaces have the potential to increase nearby housing premiums.
+
+![Overview of study area](Paper/figures/study_area.png)
+
+### Data
+
+In this study, property listings were obtained from Funda.nl, a Dutch online real-estate platform [30].
+Here, data included the sale price and property characteristics of residential houses in Amsterdam listed on the platform on 31 March 2023.
+Moreover, information about multiple public amenities in Amsterdam were obtained from a variety of sources, including ArcGIS [31], OpenStreetMap.org [32, 33] and the municipality of Amsterdam [34].
+Selection of public amenities, used as controlling variables, were based on applicable literature, as presented in Table 1.
+Adjusting for these variables was done to limit the effect of potential confounders on the association of interest.
+Finally, remote sensing images in red and near-infrared were obtained from Sentinel-2 in August 2022 [35].
+This allowed on the capitalisation of high greenness levels in that period, leading to improved differentiation between green and urban areas.
+
+### Data Enrichtment
+
+![Illustrative figure of using focal statistics as a buffer function](Paper/figures/raster5.png)
 

### 2023-04-07 Paper/paper.Rmd
readme update
update

@@
   \titlespacing{\subsubsection}{0pt}{5pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
+  \usepackage{geometry}
+  \geometry{left=1.5cm,right=1.5cm}
 mainfont: Cambria
@@
 
-```{=latex}
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{figures/raster5.png}
-  \caption{Illustrative figrue of the focal statistics as buffer distance.}
-\end{figure}
-```
+To examine the economic value of urban green spaces as reflected in the real-estate prices, coordinates for each property were obtained using geocoding and transformed into a single coordinate reference system, i.e.
+EPSG 28992, to ensure consistency and accuracy of the analysis.
+Exclusion criteria were in place for properties for which coordinates could not be obtained, i.e.
+future housing projects.
+Moreover, straight line distances from each property to the nearest public amenities were enumerated using the nearest neighbour algorithm in combination with Euclidean distance.
+This is a common approach to adjust for the implicit premium of local public amenities on house prices.
+
+Furthermore, urban green vegetation was measured using NDVI.
+This vegetation index was derived from the Sentinel-2 satellite, as expressed in Equation 1.
+Here, N and R refer to the spectral reflectance measurements obtained in the red and near-infrared regions, respectively.
+In general, the index ranges from -1.0 to 1.0 with positive values indicating greenness.
+The usage of this remote sensing system provided more accurate images for identifying green spaces, i.e.
+10x10m, compared to the moderate resolution of Landsat, i.e.
+30x30m.
+
+Surrounding the residential properties, mean values of NDVI were obtained at varying spatial scales, i.e.
+100, 300 and 500m.
+In doing so, the variation of greenness around the property was included in the analysis.
+Moreover, the usage of these particular thresholds ensured that the results were less vulnerable to scaling effects given the resolution of the input data.
+Finally, based on the extraction and enhancement of data, several independent variables were identified and constructed, as presented in Table 1.
+These variables were included in the hedonic pricing model, as will be elaborated on in Section 2.4, to either adjust or explain the economic value of urban green areas in Amsterdam.
+
 ## 2.4 Analysis
@@
 ```{=latex}
-\begin{table}[]
+\begin{table*}[b]
 \centering
-\caption{Included variables}
-\begin{tabular}{@{}lll@{}}
+\caption{Descriptive Statistics of Property, Public Amenity and Greenness Characteristics of Properties in  Amsterdam.}
+\begin{tabular}{@{}llll@{}}
 \toprule
-Variable            & Mean (n = 1719) & SD \\ \midrule
-Living area (m2)    & 105.7           & 71.0               \\
-Bedroom (N)         & 2.5             & 1.4                \\
-Bathroom (N)        & 1.1             & 0.7                \\
-House age (Years)   & 76.9            & 63.2               \\
-Train distance (m)  & 1703.7          & 958.2              \\
-Metro distance (m)  & 1303.2          & 951.8              \\
-Tram distance (m)   & 689.1           & 1024.7             \\
-NDVI 300m range     & 0.212           & 0.069              \\
-Centre distance (m) & 3770.5          & 2288.1             \\
-Zuid distance (m)   & 4659.2          & 2228.3             \\
-School distance (m) & 268.3           & 183.8              \\
-Shops distance (m)  & 266.7           & 206.9              \\
-                    &                 &                    \\ \bottomrule
-
+\textbf{Independent Variable}      & \textbf{Mean} & \textbf{SD} & \textbf{Description}                        \\ \midrule
+\multicolumn{4}{c}{\textbf{Summary Statistics (N = 1,719)}}                                                    \\ \midrule
+\textbf{Property Characteristics}  &               &             &                                             \\
+Living Area (m2)                   & 105.7         & 71.0        & Size of livable area of the property        \\
+Number of Bedrooms                 & 2.5           & 1.4         & Number of bedrooms of the property          \\
+Number of Bathrooms                & 1.1           & 0.7         & Number of bathrooms of the property         \\
+House Age (years)                  & 76.9          & 63.2        & Age of the property in 2023                 \\
+\textbf{Design}                    &               &             &                                             \\
+NDVI100                            & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
+NDVI300                            & 0.212         & 0.069       & Average NDVI at 300 m around property       \\
+NDVI500                            & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
+\textbf{Transit Distance}          &               &             &                                             \\
+Distance to Train Station (m)      & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
+Distance to Tram Station (m)       & 689.1         & 1024.7      & Euclidean distance to nearest tram station  \\
+Distance to Metro Station (m)      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
+\textbf{Destination Accessibility} &               &             &                                             \\
+Distance to City Center (m)        & 3770.5        & 2288.1      & Euclidean distance to city center           \\
+Distance to Business District (m) & 4659.2 & 2228.3 & Euclidean distance to business district \\
+Distance to School (m)             & 268.3         & 183.8       & Euclidean distance to nearest school        \\
+Distance to Convenience Stores (m) & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}
 ```

### 2023-04-10 Paper/paper.Rmd
paper
paper update

@@
 
-```{r include=FALSE}
-#all code for plots
-library(mapview)
-library(tidyverse)
-library(tmap)
-library(sf)
-setwd("./..")
-funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
-PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
-setwd("Paper")
-```
-
 # 1. Introduction
@@
 
-A review of literature revealed that there are several studies that aimed to examine the effect of urban green spaces on residential house prices [13–19].
+A review of literature revealed several studies that aimed to examine the effect of urban green spaces on residential house prices [13–19].
 Often these studies adopted a hedonic pricing approach to estimate the economic value that individuals place on particular property characteristics, as reflected in the real-estate prices [14, 15].
 However, most literature only focused on the distance to urban green areas as a valuation indicator [20, 21].
-Here, a few studies considered a more comprehensive appreciation of greenness in cities by employing vegetation indices and the interaction with property and public amenities [16, 17, 22, 23].
+Only a few studies considered a more comprehensive appreciation of greenness in cities by employing vegetation indices and the interaction with property and public amenities [16, 17, 22, 23].
 
@@
 Moreover, most of these studies also considered the interaction with residential and public amenities, such as the number of rooms or proximity to convenience stores [16, 23].
-However, these analyses were mainly performed in cities with conservative urban greening programs in place [23].
+However, these analyses were mainly performed in cities with conservative greening programs in place [23].
 Lastly, the adoption of NDVI for identifying (urban) green spaces is often criticised due to its sensitivity to varying spatial scales and inability to differentiate between vegetation types [24].
@@
 
-Based on the examined literature, a hedonic pricing approach in combination with the normalised difference vegetation index and the interaction with particular amenities emerges as an effective method to estimate the effect of urban green spaces on residential house prices.
-Given the limited literature available on property value premiums associated with greenness exposure in cities with more progressive urban greening programs, this study aims to answer the research question of what the economic value of urban green spaces in the city of Amsterdam is in the year 2023, as reflected in the real-estate prices.
+Based on the examined literature, a hedonic pricing approach in combination with NDVI and the interaction with particular amenities emerges as an effective method to estimate the effect of urban green spaces on residential house prices.
+Given the limited literature available on property value premiums associated with greenness exposure in cities with more progressive urban greening programs, this study aims to answer the research question of what the economic value of urban green spaces is in the city of Amsterdam, as reflected in the real-estate prices of 2023.
 
@@
 The geographical scope in this study concentrated on the city of Amsterdam, as presented in Figure 1.
-The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27] that occupy a space of 219.3 km2  [28].
-As a result, the city is considered one of the most densely populated in the country.
+The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27], occupying a space of 219.3 km2  [28].
 Surrounding the residential areas, the vast majority of land is occupied with vegetation [29].
 Moreover, the municipality has progressive urban greening programs in place, stimulating and obligating residents and city districts to participate in greening initiatives [12].
-As a result, these policies aimed at expanding urban green spaces have the potential to increase nearby housing premiums.
+As a result, these policies aimed at expanding urban green spaces may have the potential to increase nearby housing premiums.
 
 ```{=latex}
-\begin{figure}[t]
+\begin{figure}[]
   \centering
@@
 
-## 2.2 Data
-In this study, property listings were obtained from Funda.nl, a Dutch online real-estate platform [30].
-Here, data included the sale price and property characteristics of residential houses in Amsterdam listed on the platform on 31 March 2023.
-Moreover, information about multiple public amenities in Amsterdam were obtained from a variety of sources, including ArcGIS [31], OpenStreetMap.org [32, 33] and the municipality of Amsterdam [34].
+## 2.2 Data Extraction
+A total of 1,719 property listings were obtained from Funda.nl, a Dutch online real-estate platform [30].
+Here, data included the sale price and property characteristics of homes in Amsterdam listed on the platform on 31 March 2023.
+Moreover, information about public amenities in Amsterdam were obtained from a variety of sources, including ArcGIS [31], OpenStreetMap.org [32, 33] and the municipality of Amsterdam [34].
 Selection of public amenities, used as controlling variables, were based on applicable literature, as presented in Table 1.
 Adjusting for these variables was done to limit the effect of potential confounders on the association of interest.
-Finally, remote sensing images in red and near-infrared were obtained from Sentinel-2 in August 2022 [35].
+Finally, remote sensing images were obtained from Sentinel-2 in August 2022 [35].
 This allowed on the capitalisation of high greenness levels in that period, leading to improved differentiation between green and urban areas.
@@
 Moreover, straight line distances from each property to the nearest public amenities were enumerated using the nearest neighbour algorithm in combination with Euclidean distance.
-This is a common approach to adjust for the implicit premium of local public amenities on house prices.
+This is a common approach to adjust for the implicit premium of local public amenities on house prices [36].
 
 Furthermore, urban green vegetation was measured using NDVI.
-This vegetation index was derived from the Sentinel-2 satellite, as expressed in Equation 1.
+This vegetation index was derived from the Sentinel-2 satellite, based on Equation 1.
 Here, N and R refer to the spectral reflectance measurements obtained in the red and near-infrared regions, respectively.
 In general, the index ranges from -1.0 to 1.0 with positive values indicating greenness.
-The usage of this remote sensing system provided more accurate images for identifying green spaces, i.e.
+The usage of this system provided more accurate images for identifying green spaces, i.e.
 10x10m, compared to the moderate resolution of Landsat, i.e.
-30x30m.
+30x30m [37].
+
+$$ NDVI= \frac{(N - R)}{N + R} $$
 
@@
 100, 300 and 500m.
-In doing so, the variation of greenness around the property was included in the analysis.
-Moreover, the usage of these particular thresholds ensured that the results were less vulnerable to scaling effects given the resolution of the input data.
+In doing so, the variation of greenness around the property could be included in the analysis.
+Moreover, the usage of these thresholds ensured that the results were less vulnerable to scaling effects given the resolution of the data [37].
 Finally, based on the extraction and enhancement of data, several independent variables were identified and constructed, as presented in Table 1.
@@
 
-## 2.4 Analysis
-
 ```{=latex}
-\begin{table*}[b]
+\begin{table*}[]
 \centering
@@
 
-## 2.4.1 Ordinary Least Squares
+## 2.4 Hedonic Pricing Models
 
-## 2.4.2 Spatial Dependence and Heterogeineity
+Two forms of the hedonic pricing model were employed to examine the effect of urban green spaces on housing prices per square meter, namely ordinary least squares (OLS) and geographically weighted regression (GWR).
+In the models, the relation of interest was adjusted for using property characteristics, transit distances and destination accessibility.
+Here, the usage of OLS was mainly related to its superior interpretability [38].
+However, the Durbin-Watson test and Variance Inflation Factor (VIF) revealed that observations were not independent and indicated some collinearity, respectively.
+Hence, violating two model assumptions [39].
+As a result, variables NDVI100 and NDVI500 were excluded from the analysis, as these resulted in considerable collinearity (VIF > 5).
+Moreover, Moran’s I indicated the presence of spatial dependency (0.590, p < 0.05), as presented in Figure 2.
 
-## 2.4.3 Geographically Weighted Regression
+```{=latex}
+\begin{figure}[]
+  \centering
+  \includegraphics[width=\linewidth]{figures/moranImc.png}
+  \caption{Density plot of Monte-Carlo Moran's I Permutation Outcomes.}
+\end{figure}
+```
+
+Furthermore, similar studies found evidence for the existence of non-stationarity in both house prices and green spaces [40, 41].
+Hence, a local regression approach, i.e.
+GWR with an adaptive bi-square kernel, was employed to account for both the spatial dependence and non-stationarity in the data.
+Here, a golden search algorithm was used to obtain the kernel bandwidth, as data was not uniformly distributed across space [42].
+Doing so, provided estimates for each location in the study area.
 
@@
 ```{=latex}
-\begin{figure*}[ht]
+\begin{table*}[]
 \centering
-  \includegraphics[width=\linewidth]{figures/ndvi_houseprices.png}
-  \caption{This is a figure.}
-\end{figure*}
+\caption{Hier caption}
+\begin{tabular}{@{}lllll@{}}
+\toprule
+\textbf{Independent Variable} &
+  \textbf{Coef.} &
+  \textbf{Min. Coef.} &
+  \textbf{Median Coef.} &
+  \textbf{Max. Coef.} \\ \midrule
+                                     & OLS1       &           & GWR1, 2 &           \\ \midrule
+\textbf{Property Characteristics}    &            &           &         &           \\
+Living Area (m2)                     & 4.7**      & -45.7     & -5.3    & 28.4      \\
+Number of Bedrooms                   & -329.6**   & -1384.2   & -136.0  & 957.8     \\
+Number of Bathrooms                  & 318.3**    & -1206.8   & 248.3   & 2,385.9   \\
+House Age (years)                    & 1.3**      & -121.1    & -0.6    & 74.1      \\
+\textbf{Design}                      &            &           &         &           \\
+NDVI300                              & -1,674.1** & -82,657.5 & 262.5   & 125,978.4 \\
+\textbf{Transit Distance}            &            &           &         &           \\
+Distance to Train Station (m)        & -0.08      & -79.7     & 1.0     & 297.5     \\
+Distance to Tram Station (m)         & 0.4**      & -38.5     & 0.2     & 45.8      \\
+Distance to Metro Station (m)        & 0.5**      & -66.0     & 0.5     & 39.1      \\
+\textbf{Destination Accessibility}   &            &           &         &           \\
+Distance to City Center (m)          & -0.5**     & -495.3    & -1.2    & 124.4     \\
+Distance to Business District   (m)  & -0.5**     & -145.6    & -0.02   & 162.1     \\
+Distance to School (m)               & 0.3        & -21.5     & -0.6    & 9.4       \\
+Distance to Convenience Stores   (m) & 1.2**      & -15.4     & 0.2     & 18.1      \\ \midrule
+Akaike Information Criterion   (AIC) & 30,487     &           & 29,720  &           \\ \midrule
+\multicolumn{5}{l}{** Significant at p \textless 0.05}                              \\
+\multicolumn{5}{l}{1 Statistical significance levels are only reported for the global OLS model,} \\
+\multicolumn{5}{l}{as p-values could not be easily presented for GWR due to its local approach.} \\
+\multicolumn{5}{l}{2 Bandwidth of adjusted kernel corresponds to 67.}              
+\end{tabular}
+\end{table*}
 ```

### 2023-04-11 3. Final analysis & Results.R
update

@@ -32,4 +32,29 @@ tm_shape(PC4, bbox = bbox_new)+
             legend.text.size = 0.75,
             legend.title.size = 1)
 
+################## create coef plot for ndvi for paper
+paper_plot <- tm_shape(PC4, bbox = bbox_new) + 
+  tm_polygons(col = 'lightgrey') + 
+  tm_shape(gwr_result %>% filter(ndvi300_TV < -1.96 | ndvi300_TV > 1.96)) + 
+  tm_dots(col = 'ndvi300', 
+          size = 0.2,
+          midpoint = 0, 
+          title = "Residential Property Premiums (in euros)",
+          palette = 'Spectral',
+          shape = 21) + 
+  tm_layout(title.position = c('center', 'top'),
+            title.fontface = 'bold',
+            title.fontfamily = 'Times',
+            legend.title.fontface = 'bold',
+            legend.title.fontfamily = 'Times',
+            legend.text.fontfamily = 'Times',
+            legend.position = c(0.03, -0.01),
+            legend.text.size = 0.5,
+            legend.title.size = 0.9,
+            frame = F)
+
+paper_plot
+
+# Save
+tmap_save(paper_plot, 'Economic_Value_Urban_Green.png', width = 5, height = 3.5)
 

### 2023-04-11 Paper/paper.Rmd
update

@@
   \usepackage{geometry}
-  \geometry{left=1.5cm,right=1.5cm}
+  \geometry{left=1.3cm,right=1.3cm}
 mainfont: Cambria
@@
 ## 2.3 Data Enrichment
-
   To examine the economic value of urban green spaces as reflected in the real-estate prices, coordinates for each property were obtained using geocoding and transformed into a single coordinate reference system, i.e.
@@
 
-$$ NDVI= \frac{(N - R)}{N + R} $$
-
+$$ NDVI= \frac{(N - R)}{(N + R)} $$
   Surrounding the residential properties, mean values of NDVI were obtained at varying spatial scales, i.e.
@@
 ## 2.4 Hedonic Pricing Models
-
   Two forms of the hedonic pricing model were employed to examine the effect of urban green spaces on housing prices per square meter, namely ordinary least squares (OLS) and geographically weighted regression (GWR).
 In the models, the relation of interest was adjusted for using property characteristics, transit distances and destination accessibility.
-Here, the usage of OLS was mainly related to its superior interpretability [38].
+Here, the usage of OLS was mainly related to its superior interpretability [40].
 However, the Durbin-Watson test and Variance Inflation Factor (VIF) revealed that observations were not independent and indicated some collinearity, respectively.
-Hence, violating two model assumptions [39].
+Hence, violating two model assumptions [41].
 As a result, variables NDVI100 and NDVI500 were excluded from the analysis, as these resulted in considerable collinearity (VIF > 5).
@@
 
-Furthermore, similar studies found evidence for the existence of non-stationarity in both house prices and green spaces [40, 41].
+  Furthermore, similar studies found evidence for the existence of non-stationarity in both house prices and green spaces [39, 42].
 Hence, a local regression approach, i.e.
 GWR with an adaptive bi-square kernel, was employed to account for both the spatial dependence and non-stationarity in the data.
-Here, a golden search algorithm was used to obtain the kernel bandwidth, as data was not uniformly distributed across space [42].
+Here, a golden search algorithm was used to obtain the kernel bandwidth, as data was not uniformly distributed across space [43].
 Doing so, provided estimates for each location in the study area.
+Finally, an overview of the scripts used throughout this study may be found on: [GitHub](https://github.com/JitseRuurd/Amsterdam_house_prices.git).
 
 # 3. Results and Discussion
+  The results showed that urban green spaces provide significant economic value, indicated by their positive association with residential property prices in the local regression model.
+However, this association was not consistent across all locations, as presented in Figure 3.
+Since the local model captured both the spatial dependence and non-stationarity present in the data, this section primarily focuses on the results of this model.
+A detailed overview of both models is presented in Appendix I.
+
+  Results of the local regression revealed that urban green spaces were significantly associated with residential house prices at a 300m spatial scale (p < 0.05).
+Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
+These results align with previous studies, highlighting the non-stationary nature of the association of interest [23, 36, 39, 40].
+As a result, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential property prices.
+
+  Moreover, the results indicated a positive association between the extent of urban green areas and residential property premiums, i.e.
+listings located near parks indicated higher premiums compared to smaller areas of greenness.
+One explanation for this finding is the direct-use value placed on these sites [23].
+In other words, more extensive green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44].
+
+  Finally, limitations of this study were three-fold.
+First, distinctions between vegetation types were not considered.
+However, it was demonstrated to affect the scope and magnitude on house prices differently [45].
+Second, the presence of property and neighbourhood characteristics that were unobserved but associated with urban green space and/or house prices may have biased the estimations.
+Lastly, the temporal dimension was not considered in this study.
+Hence, this may limit the generalisability of the study as the dynamic nature of the data might not be captured.
+
+```{=latex}
+\begin{figure}[]
+  \centering
+  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
+  \caption{Overview of Statistically Significant Urban Green Space Coefficients, i.e. NDVI at a 300m Spatial Scale, (p < 0.05) in Amsterdam.}
+\end{figure}
+```
+
+# 4. Conclusion
+  This study aimed to examine the economic value of urban green spaces in Amsterdam, as reflected in the real-estate prices of 2023.
+Here, property characteristics, public amenities and greenness measurements were obtained from a variety of sources.
+In line with topical literature, independent variables were identified and constructed to either adjust or explain the economic value of urban green spaces.
+In doing so, the local hedonic pricing model revealed that urban green spaces provided significant economic value.
+However, this association was not consistent across all locations, as the property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
+The main theoretical explanation for this range might be related to the direct-use value placed on these areas.
+As a result, the outcomes of this study provide empirical evidence for the capitalisation of greenness characteristics in residential real-estate.
+
+# 5. References
+
+# Appendix I
 
@@
 ```
-
-# 4. Conclusion
-
-# 5. References

### 2023-04-11 3. Final analysis & Results.R
Update 3. Final analysis & Results.R

@@ -33,7 +33,7 @@ tm_shape(PC4, bbox = bbox_new)+
             legend.title.size = 1)
 
 ################## create coef plot for ndvi for paper
-paper_plot <- tm_shape(PC4, bbox = bbox_new) + 
+paper_plot <- tm_shape(PC4) + 
   tm_polygons(col = 'lightgrey') + 
   tm_shape(gwr_result %>% filter(ndvi300_TV < -1.96 | ndvi300_TV > 1.96)) + 
   tm_dots(col = 'ndvi300', 

### 2023-04-11 3. Final analysis & Results.R
update

@@ -1,8 +1,9 @@
-easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep")
+easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep", 'stars')
 
 #Visualize results GWR model
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
+ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
 
 #plot variables of interest
 # Extend bbox for plots
@@ -10,9 +11,9 @@ bbox_new <- st_bbox(PC4) # current bounding box
 xrange <- bbox_new$xmax - bbox_new$xmin # range of x values 
 yrange <- bbox_new$ymax - bbox_new$ymin # range of y values 
 # bbox_new[1] <- bbox_new[1] - (0.25 * xrange) # xmin - left 
-bbox_new[3] <- bbox_new[3] + (0.25 * xrange) # xmax - right 
+bbox_new[3] <- bbox_new[3] + (0 * xrange) # xmax - right 
 # bbox_new[2] <- bbox_new[2] - (0.25 * yrange) # ymin - bottom 
-bbox_new[4] <- bbox_new[4] + (0.25 * yrange) # ymax - top 
+bbox_new[4] <- bbox_new[4] + (0 * yrange) # ymax - top 
 bbox_new <- bbox_new %>%
   st_as_sfc() 
 
@@ -57,4 +58,19 @@ paper_plot
 
 # Save
 tmap_save(paper_plot, 'Economic_Value_Urban_Green.png', width = 5, height = 3.5)
+
+################## create plot for ndvi for paper
+tm_shape(ndvi, bbox = bbox_new)+
+  tm_raster(palette = "YlGn", title = "NDVI") +
+  tm_shape(PC4, bbox = bbox_new)+
+  tm_polygons(col = "white", alpha = 0, border.col = "black")+
+  tm_layout(title.fontfamily = "Times",
+            title.fontface = "bold",
+            legend.text.fontfamily = "Times",
+            legend.title.fontfamily = "Times",
+            legend.text.size = 0.75,
+            legend.title.size = 1,
+            frame = F,
+            legend.outside.position = c('right', 'center'),
+            legend.outside = T)
 

### 2023-04-11 Paper/paper.Rmd
paper update

@@
 bibliography: references.bib
-csl: apa.csl
-
+indent: true
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
+knitr::opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)
 
@@
 \multicolumn{4}{c}{\textbf{Summary Statistics (N = 1,719)}}                                                    \\ \midrule
-\textbf{Property Characteristics}  &               &             &                                             \\
+\textbf{Property Characteristics$^1$}  &               &             &                                             \\
 Living Area (m2)                   & 105.7         & 71.0        & Size of livable area of the property        \\
@@
 House Age (years)                  & 76.9          & 63.2        & Age of the property in 2023                 \\
-\textbf{Design}                    &               &             &                                             \\
+\textbf{Design$^2$}                    &               &             &                                             \\
 NDVI100                            & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
@@
 NDVI500                            & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
-\textbf{Transit Distance}          &               &             &                                             \\
+\textbf{Transit Distance$^{3,4,5}$} &               &             &                                             \\
 Distance to Train Station (m)      & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
@@
 Distance to Metro Station (m)      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
-\textbf{Destination Accessibility} &               &             &                                             \\
+\textbf{Destination Accessibility$^4$} &               &             &                                             \\
 Distance to City Center (m)        & 3770.5        & 2288.1      & Euclidean distance to city center           \\
@@
 Distance to Convenience Stores (m) & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
+\multicolumn{4}{l}{Sources: $^1$Funda.nl, $^2$Sentinel-2, $^3$ArcGIS, $^4$OpenStreetMap.org, and $^5$Amsterdam Municipality} 
 \end{tabular} 
@@
 Doing so, provided estimates for each location in the study area.
-Finally, an overview of the scripts used throughout this study may be found on: [GitHub](https://github.com/JitseRuurd/Amsterdam_house_prices.git).
+Finally, an overview of the scripts used throughout this study may be found on: [GitHub](https://github.com/JitseRuurd/Amsterdam_Urban_Green.git).
 
@@
 Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
-These results align with previous studies, highlighting the non-stationary nature of the association of interest [23, 36, 39, 40].
+These results align with previous studies, highlighting the non-stationary nature of the association of interest [23, 36, 39, 40], as illustrated in Appendix II.
 As a result, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential property prices.
@@
 # 5. References
+```{=latex}
+\begin{enumerate}
+\item Morancho AB (2003) A hedonic valuation of urban green areas. Landsc Urban Plan 66:35–41. https://doi.org/10.1016/S0169-2046(03)00093-8
+
+\item Selmi W, Weber C, Rivière E, et al (2016) Air pollution removal by trees in public green spaces in Strasbourg city, France.
+Urban For Urban Green 17:192–201.
+https://doi.org/10.1016/j.ufug.2016.04.010
+
+\item Georgi JN, Dimitriou D (2010) The contribution of urban green spaces to the improvement of environment in cities: Case study of Chania, Greece.
+Build Environ 45:1401–1414.
+https://doi.org/10.1016/j.buildenv.2009.12.003
+
+\item Wang C, Ren Z, Dong Y, et al (2022) Efficient cooling of cities at global scale using urban green space to mitigate urban heat island effects in different climatic regions.
+Urban For Urban Green 74:127635.
+https://doi.org/10.1016/j.ufug.2022.127635
+
+\item Shishegar N (2014) The Impacts of Green Areas on Mitigating Urban Heat Island Effect.
+The International Journal of Environmental Sustainability 9:119–130.
+https://doi.org/10.18848/2325-1077/CGP/v09i01/55081
+
+\item Huang M, Cui P, He X (2018) Study of the Cooling Effects of Urban Green Space in Harbin in Terms of Reducing the Heat Island Effect. Sustainability 10:1101. https://doi.org/10.3390/su10041101
+
+\item Jim CY, Chen WY (2006) Perception and Attitude of Residents Toward Urban Green Spaces in Guangzhou (China). Environ Manage 38:338–349. https://doi.org/10.1007/s00267-005-0166-6
+
+\item Groenewegen PP, van den Berg AE, de Vries S, Verheij RA (2006) Vitamin G: effects of green space on health, well-being, and social safety.
+BMC Public Health 6:149.
+https://doi.org/10.1186/1471-2458-6-149
+
+\item Ayala-Azcárraga C, Diaz D, Zambrano L (2019) Characteristics of urban parks and their relation to user well-being. Landsc Urban Plan 189:27–35. https://doi.org/10.1016/j.landurbplan.2019.04.005
+
+\item Department of Environmental Protection (2021) NYC Green Infrastructure. New York City
+
+\item Lachmund J (2013) Greening Berlin. The MIT Press
+
+\item Department of Planning and Sustainability (2020) Amsterdam Green Infrastructure Vision 2050. Amsterdam
+
+\item Conway D, Li CQ, Wolch J, et al (2010) A Spatial Autocorrelation Approach for Examining the Effects of Urban Greenspace on Residential Property Values.
+The Journal of Real Estate Finance and Economics 41:150–169.
+https://doi.org/10.1007/s11146-008-9159-6
+\item Saphores J-D, Li W (2012) Estimating the value of urban green areas: A hedonic pricing analysis of the single family housing market in Los Angeles, CA.
+Landsc Urban Plan 104:373–387.
+https://doi.org/10.1016/j.landurbplan.2011.11.012
+
+\item Panduro TE, Veie KL (2013) Classification and valuation of urban green spaces—A hedonic house price valuation. Landsc Urban Plan 120:119–128. https://doi.org/10.1016/j.landurbplan.2013.08.009
+
+\item Holt JR, Borsuk ME (2020) Using Zillow data to value green space amenities at the neighborhood scale. Urban For Urban Green 56:126794. https://doi.org/10.1016/j.ufug.2020.126794
+
+\item Zambrano-Monserrate MA, Ruano MA, Yoong-Parraga C, Silva CA (2021) Urban green spaces and housing prices in developing countries: A Two-stage quantile spatial regression analysis.
+For Policy Econ 125:102420.
+https://doi.org/10.1016/j.forpol.2021.102420
+
+\item Sander H, Polasky S, Haight RG (2010) The value of urban tree cover: A hedonic property price model in Ramsey and Dakota Counties, Minnesota, USA.
+Ecological Economics 69:1646–1656.
+https://doi.org/10.1016/j.ecolecon.2010.03.011
+
+\item Sander HA, Haight RG (2012) Estimating the economic value of cultural ecosystem services in an urbanizing area using hedonic pricing.
+J Environ Manage 113:194–205.
+https://doi.org/10.1016/j.jenvman.2012.08.031
+
+\item Czembrowski P, Kronenberg J (2016) Hedonic pricing and different urban green space types and sizes: Insights into the discussion on valuing ecosystem services.
+Landsc Urban Plan 146:11–19.
+https://doi.org/10.1016/j.landurbplan.2015.10.005
+
+\item Anderson ST, West SE (2006) Open space, residential property values, and spatial context. Reg Sci Urban Econ 36:773–789. https://doi.org/10.1016/j.regsciurbeco.2006.03.007
+
+\item Li W, Saphores J-DM, Gillespie TW (2015) A comparison of the economic benefits of urban green spaces estimated with NDVI and with high-resolution land cover data.
+Landsc Urban Plan 133:105–117.
+https://doi.org/10.1016/j.landurbplan.2014.09.013
+
+\item Mei Y, Zhao X, Lin L, Gao L (2018) Capitalization of Urban Green Vegetation in a Housing Market with Poor Environmental Quality: Evidence from Beijing.
+J Urban Plan Dev 144:.
+https://doi.org/10.1061/(ASCE)UP.1943-5444.0000458
+
+\item Martinez A de la I, Labib SM (2023) Demystifying normalized difference vegetation index (NDVI) for greenness exposure assessments and policy interventions in urban greening.
+Environ Res 220:115155.
+https://doi.org/10.1016/j.envres.2022.115155
+
+\item Rhew IC, Vander Stoep A, Kearney A, et al (2011) Validation of the Normalized Difference Vegetation Index as a Measure of Neighborhood Greenness.
+Ann Epidemiol 21:946–952.
+https://doi.org/10.1016/j.annepidem.2011.09.001
+
+\item Jimenez RB, Lane KJ, Hutyra LR, Fabian MP (2022) Spatial resolution of Normalized Difference Vegetation Index and greenness exposure misclassification in an urban cohort.
+J Expo Sci Environ Epidemiol 32:213–222.
+https://doi.org/10.1038/s41370-022-00409-w
+
+\item CBS Statline (2022) Inwoners per Gemeente. In: Centraal Bureau voor de Statistiek. https://www.cbs.nl/nl-nl/visualisaties/dashboard-bevolking/regionaal/inwoners. Accessed 6 Apr 2023
+
+28. 	CBS Statline (2022) Kerncijfers wijken en buurten 2022. In: Centraal Bureau voor de Statistiek. https://opendata.cbs.nl. Accessed 6 Apr 2023
+
+\item Department of Planning and Sustainability (2018) Evaluatie project Groen in de buurt. Amsterdam
+
+\item Funda (2023) Zoek huizen en appartementen te koop in Nederland. https://www.funda.nl. Accessed 6 Apr 2023
+
+\item ArcGIS (2021) Stations in Nederland. https://www.arcgis.com/home. Accessed 6 Apr 2023
+
+\item OpenStreetMap Contributors (2023) Convenience Store Amenities. In: OpenStreetMap.org
+
+\item OpenStreetMap Contributors (2023) School Amenities. In: OpenStreetMap.org
+
+\item Municipality of Amsterdam (2023) Datacatalogus. https://data.amsterdam.nl/datasets/zoek/. Accessed 6 Apr 2023
+
+\item European Space Agency (2022) Sentinel-2 Level-2A. https://planetarycomputer.microsoft.com/dataset/sentinel-2-l2a. Accessed 6 Apr 2023
+
+\item Daams MN, Sijtsma FJ, Veneri P (2019) Mixed monetary and non-monetary valuation of attractive urban green space: A case study using Amsterdam house prices.
+Ecological Economics 166:106430.
+https://doi.org/10.1016/j.ecolecon.2019.106430
+
+\item Labib SM, Lindley S, Huck JJ (2021) Estimating multiple greenspace exposure types and their associations with neighbourhood premature mortality: A socioecological study.
+Science of The Total Environment 789:147919.
+https://doi.org/10.1016/j.scitotenv.2021.147919
+
+\item Chen Y, Jones CA, Dunse NA, et al (2023) Housing Prices and the Characteristics of Nearby Green Space: Does Landscape Pattern Index Matter?
+Evidence from Metropolitan Area.
+Land (Basel) 12:496.
+https://doi.org/10.3390/land12020496
+
+\item Zhang S, Wang L, Lu F (2019) Exploring Housing Rent by Mixed Geographically Weighted Regression: A Case Study in Nanjing. ISPRS Int J Geoinf 8:431. https://doi.org/10.3390/ijgi8100431
+
+\item Sisman S, Aydinoglu AC (2022) A modelling approach with geographically weighted regression methods for determining geographic variation and influencing factors in housing price: A case in Istanbul.
+Land use policy 119:106183.
+https://doi.org/10.1016/j.landusepol.2022.106183
+
+\item Kasmaoui K (2019) Linear Regression. In: Global Encyclopedia of Public Administration, Public Policy, and Governance. Springer International Publishing, Cham, pp 1–11
+
+\item Wu C, Du Y, Li S, et al (2022) Does visual contact with green space impact housing pricesʔ An integrated approach of machine learning and hedonic modeling based on the perception of green space.
+Land use policy 115:106048.
+https://doi.org/10.1016/j.landusepol.2022.106048
+
+\item Suryowati K, Ranggo MO, Bekti RD, et al (2021) Geographically Weighted Regression using Fixed and Adaptive Gaussian Kernel Weighting for Maternal Mortality Rate Analysis.
+In: 2021 3rd International Conference on Electronics Representation and Algorithm (ICERA).
+IEEE, pp 115–120
+
+\item Lin I-H, Wu C, De Sousa C (2013) Examining the economic impact of park facilities on neighboring residential property values.
+Applied Geography 45:322–331.
+https://doi.org/10.1016/j.apgeog.2013.10.003
+
+\item Crompton JL (2001) The Impact of Parks on Property Values: A Review of the Empirical Evidence. J Leis Res 33:1–31. https://doi.org/10.1080/00222216.2001.11949928
+\end{enumerate}
+```
+\onecolumn
 
@@
 \centering
-\caption{Hier caption}
+\caption{Coefficients and Statistical Significance of the Ordinary Least Squares and Geographically Weighted Regression Models.}
 \begin{tabular}{@{}lllll@{}}
@@
   \textbf{Max. Coef.} \\ \midrule
-                                     & OLS1       &           & GWR1, 2 &           \\ \midrule
+                                     & OLS$^1$ &           & GWR$^{1,2}$ &           \\ \midrule
 \textbf{Property Characteristics}    &            &           &         &           \\
@@
 \multicolumn{5}{l}{** Significant at p \textless 0.05}                              \\
-\multicolumn{5}{l}{1 Statistical significance levels are only reported for the global OLS model,} \\
+\multicolumn{5}{l}{$^1$ Statistical significance levels are only reported for the global OLS model,} \\
 \multicolumn{5}{l}{as p-values could not be easily presented for GWR due to its local approach.} \\
-\multicolumn{5}{l}{2 Bandwidth of adjusted kernel corresponds to 67.}              
+\multicolumn{5}{l}{$^2$ Bandwidth of adjusted kernel corresponds to 67.}              
 \end{tabular}
@@
 ```
+
+\newpage
+
+# Appendix II
+
+```{=latex}
+\begin{figure}[]
+  \centering
+  \includegraphics[width=.8\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
+  \caption{Overview of Statistically Significant Urban Green Space Coefficients, i.e. NDVI at a 300m Spatial Scale, (p < 0.05) in Amsterdam.}
+\end{figure}
+```

### 2023-04-11 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
directory clean-up

--- 2023-04-11 Paper/paper.Rmd
@@
   - Yúri Grings
+  - Jitse Ruurd Nauta
   - Thomas Nibbering
-  - Jitse Ruurd Nauta
-date: "2023-03-21"
+
+date: "2023-04-14"
 
@@
   \usepackage{geometry}
-  \geometry{left=1.3cm,right=1.3cm}
+  \geometry{left=1.31cm,right=1.31cm}
 mainfont: Cambria
-bibliography: references.bib
 indent: true
@@
 knitr::opts_chunk$set(tidy.opts=list(width.cutoff=30),tidy=TRUE)
-
 ```
@@
 \textbf{Property Characteristics$^1$}  &               &             &                                             \\
-Living Area (m2)                   & 105.7         & 71.0        & Size of livable area of the property        \\
-Number of Bedrooms                 & 2.5           & 1.4         & Number of bedrooms of the property          \\
-Number of Bathrooms                & 1.1           & 0.7         & Number of bathrooms of the property         \\
-House Age (years)                  & 76.9          & 63.2        & Age of the property in 2023                 \\
+Living Area (m2) [38]                   & 105.7         & 71.0        & Size of livable area of the property        \\
+Number of Bedrooms [38, 39]                & 2.5           & 1.4         & Number of bedrooms of the property          \\
+Number of Bathrooms [23]               & 1.1           & 0.7         & Number of bathrooms of the property         \\
+House Age (years) [23, 38]            & 76.9          & 63.2        & Age of the property in 2023                 \\
 \textbf{Design$^2$}                    &               &             &                                             \\
-NDVI100                            & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
-NDVI300                            & 0.212         & 0.069       & Average NDVI at 300 m around property       \\
-NDVI500                            & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
+NDVI$_{100}$ [36, 39, 40]                & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
+NDVI$_{300}$ [36, 39, 40]                & 0.212         & 0.069       & Average NDVI at 300 m around property       \\
+NDVI$_{500}$ [36, 39, 40]               & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
 \textbf{Transit Distance$^{3,4,5}$} &               &             &                                             \\
-Distance to Train Station (m)      & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
-Distance to Tram Station (m)       & 689.1         & 1024.7      & Euclidean distance to nearest tram station  \\
-Distance to Metro Station (m)      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
+Distance to Train Station (m) [22]     & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
+Distance to Tram Station (m) [22]      & 689.1         & 1024.7      & Euclidean distance to nearest tram station  \\
+Distance to Metro Station (m) [23]      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
 \textbf{Destination Accessibility$^4$} &               &             &                                             \\
-Distance to City Center (m)        & 3770.5        & 2288.1      & Euclidean distance to city center           \\
-Distance to Business District (m) & 4659.2 & 2228.3 & Euclidean distance to business district \\
-Distance to School (m)             & 268.3         & 183.8       & Euclidean distance to nearest school        \\
-Distance to Convenience Stores (m) & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
+Distance to City Center (m) [38]       & 3770.5        & 2288.1      & Euclidean distance to city center           \\
+Distance to Business District (m) [38] & 4659.2 & 2228.3 & Euclidean distance to business district \\
+Distance to School (m) [23]            & 268.3         & 183.8       & Euclidean distance to nearest school        \\
+Distance to Convenience Stores (m) [38] & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
 \multicolumn{4}{l}{Sources: $^1$Funda.nl, $^2$Sentinel-2, $^3$ArcGIS, $^4$OpenStreetMap.org, and $^5$Amsterdam Municipality} 
@@
 Hence, violating two model assumptions [41].
-As a result, variables NDVI100 and NDVI500 were excluded from the analysis, as these resulted in considerable collinearity (VIF > 5).
+As a result, variables NDVI$_{100}$ and NDVI$_{500}$ were excluded from the analysis, as these resulted in considerable collinearity (VIF > 5).
 Moreover, Moran’s I indicated the presence of spatial dependency (0.590, p < 0.05), as presented in Figure 2.
@@
 Doing so, provided estimates for each location in the study area.
-Finally, an overview of the scripts used throughout this study may be found on: [GitHub](https://github.com/JitseRuurd/Amsterdam_Urban_Green.git).
+Finally, an overview of the scripts used throughout this study may be found on: [GitHub](https://github.com/JitseRuurd/Amsterdam_Urban_Green).
 
@@
 ```
-\onecolumn
+\onecolumn \newpage
 
@@
 ```{=latex}
-\begin{table*}[]
+\begin{table*}[ht]
 \centering
@@
 \textbf{Design}                      &            &           &         &           \\
-NDVI300                              & -1,674.1** & -82,657.5 & 262.5   & 125,978.4 \\
+NDVI$_{300}$                              & -1,674.1** & -82,657.5 & 262.5   & 125,978.4 \\
 \textbf{Transit Distance}            &            &           &         &           \\
@@
 ```{=latex}
-\begin{figure}[]
+\begin{figure}[ht]
   \centering
-  \includegraphics[width=.8\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
-  \caption{Overview of Statistically Significant Urban Green Space Coefficients, i.e. NDVI at a 300m Spatial Scale, (p < 0.05) in Amsterdam.}
+  \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
+  \caption{Overview of Greenness Measurements in the Form of NDVI across the City of Amsterdam.}
 \end{figure}

### 2023-04-11 README.Rmd
spelling mistake
update readme

--- 2023-03-30 README.Rmd
@@
 ---
-title: "Explaining Noord-Holland house prices"
+title: "Explaining Amsterdam House Prices with Greenness"
+subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression"
 author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
-date: "2023-03-21"
 
@@
 ---
-
 ```{r setup, include=FALSE}
@@
 
-A Spatial Statistics and Spatial Machine Learning approach.
+This study served as our term project performed at the end of the course Spatial Statistics and Machine Learning.
 
-Below the structure, results, and some code of our research can be found.
+Below a short overview of the structure of the GitHub page, methodology, data sources, and code is provided.
+
+Full paper can be found in the directory [here](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Paper/Term-Project---Grings%2C-Nauta%2C-Nibbering.pdf)!
 
@@
 
-## We used the Funda-Scraper package to scrape our data
+# Stucture of the directory
+The way the data analysis was performed is described in the figure below. Below headers provide some insight into the steps that were taken during each phase.
 
-The query below was used to scrape our final research data on (28-03-2023).
+![Overview of study area](Paper/figures/Methods.jpg)
 
-```{python eval = FALSE}
-scraper = FundaScraper(area="provincie-noord-holland", want_to="buy", find_past=False,\
-n_pages = 1000)
+## Data Extraction
+
+The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in [the 1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).
+
+The House price data was extracted with the help of the Funda-Scraper package.
+This code was however modified to be able to extract a more precise adress line, which could be used for geocoding the adress to spatial data.
+
+The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced funda scraper in the site-packages or dist-packages directory of python:
+
+```{python eval = F}
+#import function to copy the scraper folder into the dist-packages or site-packages libraries
+from copy_scraper import copy_scraper
+copy_scraper()
+```
+
+To extract the data for this project, below query was used:
+
+```{python eval = F}
+####
+# 2. Data
+####
+# Obtain Data
+scraper = FundaScraper(area="amsterdam", want_to="buy", find_past=False, n_pages = 1000)
 df = scraper.run()
 ```
-Note that this is not the original Funda-Scraper code underneath.
-The Function is adjusted to contain additional adress information, compared to the origional function.
-Code is included in the Scraper.ipynb file to copy the updated package into the site-packages directory of python.
 
-## A pre-processing pipeline is used to enrich data
+Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb):
 
-OSM was used to enrich the scraped data. We geocode adressess into geometries objects for in order to make use of the geospatial models.
-Additional spatial data includes:
+```{python eval = F}
+####
+# 1. Obtain Data
+####
+# Define Catalog
+catalog = pystac_client.Client.open("https://planetarycomputer.microsoft.com/api/stac/v1",modifier=planetary_computer.sign_inplace)
 
-* Distance to public transport (Bus, Subway, and Train)
-* Distance to public services (Schools, Universities, Shopping centres)
+# Obtain Area of Interest
+bbox_of_interest = [4.541943,52.193249,5.212109,52.532048] 
+time_of_interest = "2022-06-01/2022-09-30"
 
-## This enriched data is used to fit an OLS model
+# Search Data
+search = catalog.search(collections=["sentinel-2-l2a"],
+                        bbox=bbox_of_interest,
+                        datetime=time_of_interest,
+                        query={"eo:cloud_cover": {"lt": 20}})
 
-### OLS on scraped data
+# Obtain Data
+items = search.item_collection()
 
-```{r eval = FALSE}
-model <- lm(price~ room + bedroom + bathroom + living_area + house_age, data = funda_data)
+# Select Item from List
+selected_item = items[4]
+
+# Obtain Bands of Interest
+data = odc.stac.stac_load([selected_item], bands = ['red', 'green', 'blue', 'nir'], bbox = bbox_of_interest).isel(time=0)
 ```
 
-### OLS on enriched data
+## Data Enhancement
 
-```{r eval = FALSE}
-model <- lm(price~ room + bedroom + bathroom + living_area + house_age + bus_dist +subway_dist + train_dist + university_dist + school_dist + mall_dist + supermarket_dist, data = funda_data)
+To then use the data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column.
+
+```{r eval = F}
+df_geo <- df %>% 
+  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4", "optional5"), " ") %>% 
+  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4, optional5),
+         addressline_zip = paste(zip, letters),
+         addresszip = paste0(address, ", ",addressline_zip, ", ", addressline_city)) %>% 
+  select(-optional1, -optional2, -optional3, -optional4, -optional5) %>% 
+  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
 ```
-
-### GWR model to adjust for spatial component in the data
-
-To look at local spatial dependence, a GWR model was fit on the data.
-
-```{python eval = FALSE}
-#Run basic GWR in parallel mode
-
-gwr_selector = Sel_BW(b_coords, b_y, b_X)
-gwr_bw = gwr_selector.search(pool = pool)
-print(gwr_bw)
-gwr_results = GWR(b_coords, b_y, b_X, gwr_bw).fit(pool = pool)
-
-```
-
-### MGWR model to adjust for spatial component in the data
-
-As it would be more realistic to have different band-widths for every feature, MGWR was used
-
-```{python eval = FALSE}
-#run MGWR in parallel mode. Note: max_iter_multi needs to be specified
-
-mgwr_selector = Sel_BW(b_coords, b_y, b_X, multi=True)
-mgwr_bw = mgwr_selector.search(pool=pool, max_iter_multi=200, criterion = "AICc") 
-print(mgwr_bw)
-mgwr_results = MGWR(b_coords, b_y, b_X, selector=mgwr_selector).fit(pool=pool)
-
-```

### 2023-04-11 README.Rmd

@@
 subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression"
-author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"
 
@@
 
-Below a short overview of the structure of the GitHub page, methodology, data sources, and code is provided.
+Below is a short overview of the structure of the GitHub page, methodology, data sources, and code.
 
@@
 
-Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb):
+Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:
 

### 2023-04-11 README.Rmd
readme

@@
 
+The goal of this research was to extimate the effect of greenness on house prices in Amsterdam.
+
 Below is a short overview of the structure of the GitHub page, methodology, data sources, and code.
@@
 
-![Overview of study area](Paper/figures/Methods.jpg)
+![Overview of methods](Paper/figures/Methods.jpg)
 
@@
 
-The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in [the 1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).
+The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in the [1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).
 
@@
 
-Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:
+Lastly, the Remote Sensing data was extracted with below code in the [1b.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:
 
@@
 
-To then use the data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column.
+The data enhancement for the public amenities was performed in the [1.c Data enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).
+The steps within this script consist of finding the nearest facility for every house regarding every public amenity included.
+
+To use the Funda.nl data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column.
+Below chunk shows this code:
 
@@
 ```
+
+The pre-processing of the Remote sensing data consists of the computation of the NDVI value.
+This was done in the [1b.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb) with below code:
+```{python eval = F}
+
+ndvi = xrspatial.multispectral.ndvi(data['nir'], data['red'])
+
+ndvi.values[ndvi.values < 0] = 0
+```
+Note that negative NDVI values where set to 0.
+
+## Hedonic pricing approach
+
+With the enhanced data, several models where used to estimate the effect of greenness on the house prices in Amsterdam.
+
+First, an OLS model was used:
+
+```{r eval = F}
+equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi300 + centre_dist + zuid_dist + shops_dist + school_dist
+
+#OLS
+model <- lm(equation, 
+            data = funda_data)
+```
+
+After checking the Linear regression assumptions (results stated in the paper), an Geographically Weighted Regression (GWR) model was used as implemented below:
+
+```{python eval = F}
+#Run basic GWR in parallel mode
+gwr_selector = Sel_BW(b_coords, b_y, b_X, kernel='bisquare')
+gwr_bw = gwr_selector.search(pool = pool, criterion = "AIC") 
+print(gwr_bw)
+gwr_results = GWR(b_coords, b_y, b_X, gwr_bw, kernel="bisquare").fit(pool = pool)
+```
+
+## Results
+
+With the final GWR model, the results of the analysis were created. The main output of the analysis was the significant coefficient map shown below.
+
+![Overview of results](Paper/Figures/Economic_Value_Urban_Green_clip.png)
+
+The interpetation and conclusion of this plot is stated in chapter 3 and 4 of the report, respectively.

### 2023-04-11 README.Rmd
readme

@@
 # Stucture of the directory
-The way the data analysis was performed is described in the figure below. Below headers provide some insight into the steps that were taken during each phase.
+The way the data analysis was performed is described in the figure below. The text after the figure provides some insight into the steps that were taken during each phase.
 
-![Overview of methods](Paper/figures/Methods.jpg)
+![Overview of methods](Paper/figures/Methods.png)
 
@@
 The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in the [1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).
+The data sources consisted of the Municipality of Amsterdam, ArGIS and OSM.
 
 The House price data was extracted with the help of the Funda-Scraper package.
-This code was however modified to be able to extract a more precise adress line, which could be used for geocoding the adress to spatial data.
+This code was however modified to be able to extract a more precise address line, which could be used for geocoding the address to spatial data.
 
-The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced funda scraper in the site-packages or dist-packages directory of python:
+The [Funda scraper notebook](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/Scraper/Scraper.ipynb) provides code to copy the code of the enhanced Funda scraper in the site-packages or dist-packages directory of python:
 
@@
 
-![Overview of results](Paper/Figures/Economic_Value_Urban_Green_clip.png)
+![Overview of results](Paper/figures/Economic_Value_Urban_Green_clip.png)
 

### 2023-04-12 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
update readme
update paper
paper update

@@
   \usepackage{geometry}
-  \geometry{left=1.31cm,right=1.31cm}
+  \geometry{left=1.3cm,right=1.3cm}
 mainfont: Cambria
@@
 However, evaluating the effects of these initiatives to justify their costs remains a challenge, partly due to data sparsity.
+\linebreak
 
@@
 Only a few studies considered a more comprehensive appreciation of greenness in cities by employing vegetation indices and the interaction with property and public amenities [16, 17, 22, 23].
+\linebreak
 
@@
 Nonetheless, the index is widely accepted and can be considered almost a standard approach [25, 26].
+\linebreak
 
@@
 This is a common approach to adjust for the implicit premium of local public amenities on house prices [36].
+\linebreak
 
@@
 
-$$ NDVI= \frac{(N - R)}{(N + R)} $$
+$$ NDVI= \frac{(N - R)}{(N + R)}  \:\:\:\:\:\:\:\:(1) $$
   Surrounding the residential properties, mean values of NDVI were obtained at varying spatial scales, i.e.
@@
 A detailed overview of both models is presented in Appendix I.
+\linebreak
 
@@
 As a result, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential property prices.
+\linebreak
 
@@
 In other words, more extensive green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44].
+\linebreak
 
@@
 
-28. 	CBS Statline (2022) Kerncijfers wijken en buurten 2022. In: Centraal Bureau voor de Statistiek. https://opendata.cbs.nl. Accessed 6 Apr 2023
+\item CBS Statline (2022) Kerncijfers wijken en buurten 2022. In: Centraal Bureau voor de Statistiek. https://opendata.cbs.nl. Accessed 6 Apr 2023
 

### 2023-04-13 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
update paper

@@
 
-  Results of the local regression revealed that urban green spaces were significantly associated with residential house prices at a 300m spatial scale (p < 0.05).
+  Results of the local regression model revealed that urban green spaces were significantly associated with residental house prices at a 300m spatial scale (p < 0.05).
 Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
-These results align with previous studies, highlighting the non-stationary nature of the association of interest [23, 36, 39, 40], as illustrated in Appendix II.
-As a result, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential property prices.
+This result aligns with previous studies [23, 36, 39, 40].
+One explanation for this wide range might be related to the direct-use value placed on these areas [23].
+In other words, particular green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44].
+Hence, highlighting the spatial variability and non-stationary nature of the association of interest, as illustrated in Appendix II.
+Finally, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential real-estate prices.
 \linebreak
 
-  Moreover, the results indicated a positive association between the extent of urban green areas and residential property premiums, i.e.
-listings located near parks indicated higher premiums compared to smaller areas of greenness.
-One explanation for this finding is the direct-use value placed on these sites [23].
-In other words, more extensive green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44].
-\linebreak
-
-  Finally, limitations of this study were three-fold.
+  Limitations of this study were three-fold.
 First, distinctions between vegetation types were not considered.
@@
 As a result, the outcomes of this study provide empirical evidence for the capitalisation of greenness characteristics in residential real-estate.
+\linebreak
+
+Further research may consider the usage of eye-level greenness in addition to aerial-view greenness, as it was demonstrated that this type of information might be an important valuation indicator of residential real-estate prices [46, 47].
+Moreover, additional studies may consider the relationship between various types of urban green vegetation and property valuations.
 
@@
 \item Crompton JL (2001) The Impact of Parks on Property Values: A Review of the Empirical Evidence. J Leis Res 33:1–31. https://doi.org/10.1080/00222216.2001.11949928
+
+\item Ki D, Lee S (2021) Analyzing the effects of Green View Index of neighborhood streets on walking time using Google Street View and deep learning.
+Landsc Urban Plan 205:103920.
+https://doi.org/10.1016/j.landurbplan.2020.103920
+
+\item Wang G (2023) The effect of environment on housing prices: Evidence from the Google Street View. J Forecast 42:288–311. https://doi.org/10.1002/for.2907
+
 \end{enumerate}

### 2023-04-13 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
paper update

@@
 \centering
-\caption{Descriptive Statistics of Property, Public Amenity and Greenness Characteristics of Properties in  Amsterdam.}
+\caption{Descriptive statistics of property characteristics, public amenities and greenness measures of Amsterdam real-estate.}
 \begin{tabular}{@{}llll@{}}
@@
   \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
-  \caption{Overview of Statistically Significant Urban Green Space Coefficients, i.e. NDVI at a 300m Spatial Scale, (p < 0.05) in Amsterdam.}
+  \caption{Overview of statistically significant (p < 0.05) urban green space coefficients at a 300m spatial scale in Amsterdam.}
 \end{figure}
@@
 \centering
-\caption{Coefficients and Statistical Significance of the Ordinary Least Squares and Geographically Weighted Regression Models.}
+\caption{Coefficients and statistical significance of the Ordinary Least Squares and Geographically Weighted Regression models.}
 \begin{tabular}{@{}lllll@{}}
@@
   \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
-  \caption{Overview of Greenness Measurements in the Form of NDVI across the City of Amsterdam.}
+  \caption{Overview of NDVI values in Amsterdam with a 300m Spatial Scale}
 \end{figure}

### 2023-04-13 3. Final analysis & Results.R
Update 3. Final analysis & Results.R

@@ -1,6 +1,7 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep", 'stars')
 
 #Visualize results GWR model
+unda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
@@ -74,3 +75,26 @@ tm_shape(ndvi, bbox = bbox_new)+
             legend.outside.position = c('right', 'center'),
             legend.outside = T)
 
+################## create plot for house prices for paper
+paper_plot_prices <- tm_shape(PC4) + 
+  tm_polygons(col = 'lightgrey') + 
+  tm_shape(funda_data) + 
+  tm_dots(col = "price_m2", 
+          size = 0.2,
+          midpoint = 0, 
+          title = "House Price sq.m. (in euros)",
+          palette = 'Spectral',
+          shape = 21) + 
+  tm_layout(title.position = c('center', 'top'),
+            title.fontface = 'bold',
+            title.fontfamily = 'Times',
+            legend.title.fontface = 'bold',
+            legend.title.fontfamily = 'Times',
+            legend.text.fontfamily = 'Times',
+            legend.position = c(0.03, -0.01),
+            legend.text.size = 0.5,
+            legend.title.size = 0.9,
+            frame = F)
+
+paper_plot_prices
+tmap_save(paper_plot_prices, 'Amsterdam_house_prices_sqm.png', width = 5, height = 3.5)

### 2023-04-14 2a. OLS & SAC.R
update

@@ -48,6 +48,33 @@ houseprices_plot <- tm_shape(PC4, bbox = bbox_new)+
 
 tmap_arrange(ndvi_plot,houseprices_plot, asp = NULL, ncol = 2)
 
+#obtain maps for paper representing spatial variability and non-stationarity
+ndvi_plot <- tm_shape(ndvi, bbox = bbox_new) + 
+             tm_raster(palette = "YlGn", title = "NDVI") +
+             tm_shape(PC4, bbox = bbox_new) + 
+             tm_polygons(col = 'white', alpha = 0, border.col = "black") + 
+             tm_layout(legend.text.fontfamily = "Times",
+                       legend.title.fontfamily = "Times",
+                       legend.outside = T,
+                       frame = F)
+ndvi_plot
+
+house_plot <- tm_shape(PC4, bbox = bbox_new) + 
+              tm_polygons(col = 'lightgrey') + 
+              tm_shape(funda_data) + 
+              tm_dots(col = 'price_m2',
+                      size = 0.1,
+                      shape = 21,
+                      palette = 'YlOrRd',
+                      title = 'Property Price (per m²)') + 
+              tm_layout(title = 'B - Property Prices'
+                        legend.text.fontfamily = "Times",
+                        legend.title.fontfamily = "Times",
+                        legend.outside = T,
+                        frame = F)
+
+house_plot
+
 #test global spatial autocorrelation with Moran's I
 funda_KNN <- knearneigh(funda_data, k=5) #Identify k nearest neighbours for spatial weights 
 funda_KNN_list <- knn2nb(funda_KNN, sym=T) #Neighbours list from knn object

### 2023-04-14 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
paper update

@@
 
-  Results of the local regression model revealed that urban green spaces were significantly associated with residental house prices at a 300m spatial scale (p < 0.05).
+Results of the local regression model revealed that urban green spaces were significantly associated with residential house prices at a 300m spatial scale (p < 0.05).
 Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
@@
 In other words, particular green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44].
-Hence, highlighting the spatial variability and non-stationary nature of the association of interest, as illustrated in Appendix II.
+Hence, highlighting the spatial dependent and non-stationary nature of the association of interest, as illustrated in Appendix II.
 Finally, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential real-estate prices.
@@
   \centering
-  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
+  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green.png}
   \caption{Overview of statistically significant (p < 0.05) urban green space coefficients at a 300m spatial scale in Amsterdam.}
@@
 
-# Appendix I
+# Appendix I - Hedonic Pricing Model Results
 
@@
 
-# Appendix II
+# Appendix II – Residential House Prices and Urban Green Spaces in Amsterdam
 
@@
   \centering
-  \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
-  \caption{Overview of NDVI values in Amsterdam with a 300m Spatial Scale}
+  \includegraphics[width=.8\linewidth]{figures/Amsterdam_house_prices_sqm.png}
+  \caption{Overview of residential house-prices (top) and mean NDVI at a 300m spatial scale (bottom) in Amsterdam.}
 \end{figure}

### 2023-04-14 Paper/Term-Project---Grings,-Nauta,-Nibbering.Rmd
update

--- 2023-04-14 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
@@
 The geographical scope in this study concentrated on the city of Amsterdam, as presented in Figure 1.
-The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27], occupying a space of 219.3 km2  [28].
+The city is situated in the Western part of the Netherlands and home to almost 880,000 residents [27], occupying a space of 219.3 km$^2$  [28].
 Surrounding the residential areas, the vast majority of land is occupied with vegetation [29].
@@
 ```{=latex}
-\begin{figure}[]
+\begin{figure}[h]
   \centering
-  \includegraphics[width=\linewidth]{figures/study_area.png}
+  \includegraphics[width=.8\linewidth]{figures/study_area.png}
   \caption{Overview of the study area.}
@@
 \textbf{Property Characteristics$^1$}  &               &             &                                             \\
-Living Area (m2) [38]                   & 105.7         & 71.0        & Size of livable area of the property        \\
+Living Area (m$^2$) [38]                   & 105.7         & 71.0        & Size of livable area of the property        \\
 Number of Bedrooms [38, 39]                & 2.5           & 1.4         & Number of bedrooms of the property          \\
@@
 Results of the local regression model revealed that urban green spaces were significantly associated with residential house prices at a 300m spatial scale (p < 0.05).
-Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
+Here, property premiums per m$^2$ ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
 This result aligns with previous studies [23, 36, 39, 40].
@@
 In doing so, the local hedonic pricing model revealed that urban green spaces provided significant economic value.
-However, this association was not consistent across all locations, as the property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
+However, this association was not consistent across all locations, as the property premiums per m$^2$ ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index.
 The main theoretical explanation for this range might be related to the direct-use value placed on these areas.
@@
 \textbf{Property Characteristics}    &            &           &         &           \\
-Living Area (m2)                     & 4.7**      & -45.7     & -5.3    & 28.4      \\
+Living Area (m$^2$)                     & 4.7**      & -45.7     & -5.3    & 28.4      \\
 Number of Bedrooms                   & -329.6**   & -1384.2   & -136.0  & 957.8     \\

### 2023-04-14 3. Final analysis & Results.R
update

@@ -1,7 +1,7 @@
 easypackages::packages("tidyverse", "sf", "mapview", "RColorBrewer", "tmap", "spdep", 'stars')
 
 #Visualize results GWR model
-unda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
+funda_data <- st_read("data/Houseprices/funda_buy_amsterdam_31-03-2023_full_distances.gpkg")
 gwr_result<- st_read("data/models/gwr_results_amsterdam_ndvi300_m2.gpkg")
 PC4 <- st_transform(st_read("data/Amsterdam/PC4.json"), crs = 28992)
 ndvi <- read_stars("data/Greenness/NDVI_Amsterdam_300m.tif")
@@ -41,7 +41,7 @@ paper_plot <- tm_shape(PC4) +
   tm_dots(col = 'ndvi300', 
           size = 0.2,
           midpoint = 0, 
-          title = "Residential Property Premiums (in euros)",
+          title = "Residential Property Premiums\n(in euros per m²)",
           palette = 'Spectral',
           shape = 21) + 
   tm_layout(title.position = c('center', 'top'),
@@ -52,7 +52,7 @@ paper_plot <- tm_shape(PC4) +
             legend.text.fontfamily = 'Times',
             legend.position = c(0.03, -0.01),
             legend.text.size = 0.5,
-            legend.title.size = 0.9,
+            legend.title.size = 0.8,
             frame = F)
 
 paper_plot
@@ -61,17 +61,18 @@ paper_plot
 tmap_save(paper_plot, 'Economic_Value_Urban_Green.png', width = 5, height = 3.5)
 
 ################## create plot for ndvi for paper
-tm_shape(ndvi, bbox = bbox_new)+
+ndvi_plot <- tm_shape(ndvi, bbox = bbox_new)+
   tm_raster(palette = "YlGn", title = "NDVI") +
   tm_shape(PC4, bbox = bbox_new)+
   tm_polygons(col = "white", alpha = 0, border.col = "black")+
   tm_layout(title.fontfamily = "Times",
             title.fontface = "bold",
+            legend.title.fontface = 'bold',
             legend.text.fontfamily = "Times",
             legend.title.fontfamily = "Times",
-            legend.text.size = 0.75,
-            legend.title.size = 1,
-            frame = F,
+            legend.text.size = 0.5,
+            legend.title.size = 0.8,
+            frame = T,
[…]
